---
title: "SMB_Fitness_Geo_Admix"
author: "Joe Gunn"
date: "6/4/2021"
output: html_document
---

## Libraries needed for analysis
```{r setup, include=FALSE}
library(readxl)
library(tidyverse)
library(cowplot)
library(nlme)
library(bbmle)
library(MuMIn)
library(lme4)

```

# Read in raw working data
```{r}
smbfit_data <- read_excel("../../raw_data/master_data/smbfit_master_data_working.xlsx")

#Convert any characters to factors or numerics depending on what they need to be
smbfit_data <- smbfit_data %>%
  mutate(tl_alive = as.numeric(tl_alive)) %>%
  mutate(prop_nor_no_hsyc = as.numeric(prop_nor_no_hsyc)) %>%
  mutate(prop_neo_no_hsyc = as.numeric(prop_neo_no_hsyc)) %>%
  mutate(hyb_status_no_hsyc = factor(hyb_status_no_hsyc)) %>%
  mutate(hyb_status = factor(hyb_status)) %>%
  mutate(dist_from_df = as.numeric(dist_from_df)) %>%
  mutate(log_dist_from_df = log10(dist_from_df)) %>%
  mutate(dist_from_hw = as.numeric(dist_from_hw))
```

## Filter datasets by river (Elk River and Big Sugar Creek)
```{r}
options(scipen = 999)

#Remove any rows with "NA"
smbfit_data_noNA <- smbfit_data %>%
  drop_na(log_dist_from_df)

##df means "Deep Ford Access Area"

smbfit_data_elk <- smbfit_data_noNA %>%
  filter(river == "ELK")

smbfit_data_bsug <- smbfit_data_noNA %>%
  filter(river == "BSUG")

```

## Plot proportion of northern ancestry as a function of distance from origin
```{r}

elk_dist_admix <- ggplot(smbfit_data_elk, aes(x = dist_from_hw, y = prop_nor_no_hsyc)) + 
  geom_point(size = 2.5) +
  geom_smooth(method = "lm", se = F, color = "black") +
  theme_set(theme_cowplot(12)) +
  labs(x = "Distance from headwaters (mm)", y = "Northern Ancestry (%)") +
  theme(axis.title = element_text(size = 20)) +
  theme(axis.text = element_text(size = 15)) +
  scale_x_continuous(expand = c(0, 0), breaks = seq(0,12000,2000)) + 
  scale_y_continuous(expand = c(0, 0)) +
  expand_limits(y = 1, x = 12500) +
  theme(axis.title.x = element_text(margin = margin(t = 10))) +
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1))
  

bsug_dist_admix <- ggplot(smbfit_data_bsug, aes(x = dist_from_df, y = prop_nor_no_hsyc)) + 
  geom_point(size = 2.5) +
  geom_smooth(method = "lm", se = F, color = "black") +
  theme_set(theme_cowplot(12)) +
  labs(x = "Distance from DFA (mm)", y = "Northern Ancestry (%)") +
  theme(axis.title = element_text(size = 20)) +
  theme(axis.text = element_text(size = 15)) +
  scale_x_continuous(expand = c(0, 0), breaks = seq(0,12000,1000)) + 
  scale_y_continuous(expand = c(0, 0)) +
  expand_limits(y = 1, x = 6500) +
  theme(axis.title.y = element_blank()) +
  theme(axis.title.x = element_text(margin = margin(t = 10))) +
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1))


smbfit_data_gen_plot <- smbfit_data_noNA %>%
  mutate(river = factor(river))

levels(smbfit_data_gen_plot$river) = c("Big Sugar Creek", "Elk River")

## plot a simple ANOVA of Northern ancestry by river
nor_admix_by_river <- ggplot(smbfit_data_gen_plot, aes(x = river, y = prop_nor_no_hsyc, fill = river)) + 
  geom_boxplot(show.legend = F, outlier.shape = NA, alpha = 0.3) +
  geom_point(position = position_jitter(width = 0.2), size = 2, color = "black", pch = 21, show.legend = F) +
  theme_set(theme_cowplot(12)) + 
  labs(x = "River", y = "Northern Ancestry (%)") +
  scale_fill_manual(values = c("grey","grey")) +
  theme(axis.title = element_text(size = 20)) +
  theme(axis.text = element_text(size = 15)) +
  theme(axis.title.y = element_blank()) +
  expand_limits(y = 1) +
  theme(axis.title.x = element_text(margin = margin(t = 10))) +
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1))

  

pdf("/Users/joegunn/Desktop/Grad_School_Stuff/Research/Projects/Smallmouth_Bass_Fitness/visualization/admixture_geo_plots/admix_by_rivers.pdf", width = 15, height = 5)

plot_grid(elk_dist_admix,
          bsug_dist_admix,
          nor_admix_by_river,
          nrow = 1)

dev.off()

```

## Run linear mixed effect models for each of the above plots, taking sex into account as a random effect
```{r}
coef(summary(lmer(prop_nor_no_hsyc ~ dist_from_df + (1|sex), data = smbfit_data_bsug)))
r.squaredGLMM(lmer(prop_nor_no_hsyc ~ dist_from_df + (1|sex), data = smbfit_data_bsug))
#p = 0.367
#R2 = 0.019

coef(summary(lmer(prop_nor_no_hsyc ~ dist_from_hw + (1|sex), data = smbfit_data_elk)))
r.squaredGLMM(lmer(prop_nor_no_hsyc ~ dist_from_hw + (1|sex), data = smbfit_data_elk))
#p = 0.445
#R2 = 0.008

summary(lmer(prop_nor_no_hsyc ~ river + (1|sex), data = smbfit_data_gen_plot))
#p = 0.526
```

## Plot proportion of individuals that are pure Northern, Pure Neosho, and Admixed by average geographic distance
```{r}

smbfit_hyb_status_proportions <- read_excel("../../raw_data/master_data/ave_hyb_status_proportions_geo.xlsx")

smbfit_hyb_status_proportions <- smbfit_hyb_status_proportions %>%
  mutate(river = factor(river))

smbfit_hyb_status_proportions_elk <- smbfit_hyb_status_proportions %>%
  filter(river == "ELK")

smbfit_hyb_status_proportions_bsug <- smbfit_hyb_status_proportions %>%
  filter(river == "BSUG")

dist_admix_indivs <- ggplot(smbfit_hyb_status_proportions, aes(x = dist, y = prop_admix)) + 
  geom_point(size = 2.5) +
  geom_smooth(method = "lm", se = F, color = "black") +
  theme_set(theme_cowplot(12)) +
  labs(x = "Average distance from DFA (mm)", y = "Proportion admixed (%)") +
  theme(axis.title = element_text(size = 20)) +
  theme(axis.text = element_text(size = 15)) +
  scale_x_continuous(expand = c(0, 0), breaks = seq(0,17500,4000)) + 
  scale_y_continuous(expand = c(0, 0)) +
  expand_limits(y = 0.6, x = 17000) +
  theme(axis.title.x = element_text(margin = margin(t = 10))) +
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1))
  
dist_nor_indivs_elk <- ggplot(smbfit_hyb_status_proportions_elk, aes(x = dist_from_hw, y = prop_nor)) + 
  geom_point(size = 2.5) +
  geom_smooth(method = "lm", se = F, color = "black") +
  theme_set(theme_cowplot(12)) +
  labs(x = "Average distance from headwaters (mm)", y = "Proportion northern (%)") +
  theme(axis.title = element_text(size = 20)) +
  theme(axis.text = element_text(size = 15)) +
  scale_x_continuous(expand = c(0, 0), breaks = seq(0,12000,2000)) + 
  scale_y_continuous(expand = c(0, 0)) +
  expand_limits(y = 0.45, x = 12000) +
  theme(axis.title.x = element_text(margin = margin(t = 10))) +
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1))

dist_nor_indivs_bsug <- ggplot(smbfit_hyb_status_proportions_bsug, aes(x = dist, y = prop_nor)) + 
  geom_point(size = 2.5) +
  geom_smooth(method = "lm", se = F, color = "black") +
  theme_set(theme_cowplot(12)) +
  labs(x = "Average distance from DFA (mm)", y = "Proportion northern (%)") +
  theme(axis.title = element_text(size = 20)) +
  theme(axis.text = element_text(size = 15)) +
  scale_x_continuous(expand = c(0, 0), breaks = seq(0,5500,1000)) + 
  scale_y_continuous(expand = c(0, 0)) +
  expand_limits(y = 0.45, x = 5500) +
  theme(axis.title.x = element_text(margin = margin(t = 10))) +
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1))


pdf("/Users/joegunn/Desktop/Grad_School_Stuff/Research/Projects/Smallmouth_Bass_Fitness/visualization/admixture_geo_plots/dist_proportion_plots.pdf", width = 15, height = 5)

plot_grid(dist_admix_indivs,
          dist_nor_indivs_elk,
          dist_nor_indivs_bsug,
          nrow = 1)

dev.off()

```

## Run linear mixed effect models for each of the above plots, taking sex into account as a random effect
```{r}

summary(lm(prop_admix ~ dist, data = smbfit_hyb_status_proportions))
#p = 0.920

summary(lm(prop_nor ~ dist, data = smbfit_hyb_status_proportions))
#p = 0.1735

summary(lm(prop_nor ~ dist, data = smbfit_hyb_status_proportions_bsug))
#p = 0.084
```