---
title: "SMB_Fitness_UNUSED"
author: "Joe Gunn"
date: "6/10/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Read in phenotype (fitness) data for total length at 2 years old
smbfit_tl_2_data <- read_excel("../../raw_data/fitness_data/smbfit_tl_2_fit_data.xlsx")

smbfit_tl_2_data <- smbfit_tl_2_data %>%
  mutate(sample_id = factor(sample_id),
         estimate = factor(estimate))

#Omit Back-calculated samples and only keep real
smbfit_tl_2_data_real <- smbfit_tl_2_data %>% 
  filter(estimate == "real")

#Start cleaning up the datasets
smbfit_tl_2_data_all <- smbfit_tl_2_data[,-c(3:4)]
smbfit_tl_2_data_real <- smbfit_tl_2_data_real[,-c(3:4)]

#Make sure that the samples with fitness data line up with the genotype data.
smbfit_gen_and_fitness_samples_all <- merge(smbfit_two_column, smbfit_tl_2_data_all, by = "sample_id")
smbfit_gen_and_fitness_samples_real <- merge(smbfit_two_column, smbfit_tl_2_data_real, by = "sample_id")

#clean up the genotype data file
smbfit_gen_data_all <- smbfit_gen_and_fitness_samples_all[,-c(30:32)]
smbfit_gen_data_all <- column_to_rownames(smbfit_gen_data_all, "sample_id")

smbfit_gen_data_real <- smbfit_gen_and_fitness_samples_real[,-c(30:32)]
smbfit_gen_data_real <- column_to_rownames(smbfit_gen_data_real, "sample_id")

#Convert genotype format to inbreedR working format
smbfit_genotypes_inbreed_all <- convert_raw(smbfit_gen_data_all)
smbfit_genotypes_inbreed_real <- convert_raw(smbfit_gen_data_real)

#Check to make sure inbreedR format is correct 
check_data(smbfit_genotypes_inbreed_all, num_ind = 81, num_loci = 14) #TRUE - All good!
check_data(smbfit_genotypes_inbreed_real, num_ind = 53, num_loci = 14) #TRUE - All good!
```

## Calculate g2 (two-locus heterozygosity disequlibrium) an expected correlation of heterozygosity and inbreeding level
```{r}
g2_smbfit_all <- g2_microsats(smbfit_genotypes_inbreed_all, nperm = 1000, nboot = 1000, CI = 0.95) # 0.151
g2_smbfit_real <- g2_microsats(smbfit_genotypes_inbreed_real, nperm = 1000, nboot = 1000, CI = 0.95) # 0.238

#g2 (identity disequilibrium) is not significant, meaning that there is not great power for detecting a heterozygosity correlation with these data.


plot(g2_smbfit_all, main = "Microsatellites",
     col = "cornflowerblue", cex.axis=0.85)

plot(g2_smbfit_real, main = "Microsatellites",
     col = "cornflowerblue", cex.axis=0.85)

# r^2 between inbreeding and heterozygosity
hf_all <- r2_hf(genotypes = smbfit_genotypes_inbreed_all, nboot = 1000, type = "msats")
plot(hf_all)

hf_real <- r2_hf(genotypes = smbfit_genotypes_inbreed_real, nboot = 1000, type = "msats")
plot(hf_real)
```

## Calculate per-individual heterozygosity and run linear models to test for HFCs for all samples (including back-calculated) and only real samples based on Total length (mm)
```{r}
#heterozygosity per individual
het_all <- sMLH(smbfit_genotypes_inbreed_all)
het_real <- sMLH(smbfit_genotypes_inbreed_real)

#variance in heterozygosity
het_all_var <- var(het_all) #0.039
het_all_real <- var(het_real) #0.040

het_data_all <- as.data.frame(het_all)
het_data_all <- rownames_to_column(het_data_all, "sample_id")

het_data_real <- as.data.frame(het_real)
het_data_real <- rownames_to_column(het_data_real, "sample_id")

het_data_all <- het_data_all %>%
  mutate(sample_id = factor(sample_id))

het_data_real <- het_data_real %>%
  mutate(sample_id = factor(sample_id))

het_fit_all <- merge(het_data_all, smbfit_tl_2_data_all,by = "sample_id")
het_fit_real <- merge(het_data_real, smbfit_tl_2_data_real,by = "sample_id")

#Run linear models to test for HFCs
hfc_all <- lm(tl_alive ~ het_all, het_fit_all)
summary(hfc_all) #p = 0.76, r2 = 0.001

hfc_real <- lm(tl_alive ~ het_real, het_fit_real)
summary(hfc_real) #p = 0.82, r2 = 0.001

```

## Plot HFCs for all data (including back-calculations) and for real data only on Total Length (mm)
```{r}
HFC_tl_all_samples <- ggplot(het_fit_all, aes(het_all, tl_alive)) + 
  geom_point() + 
  geom_smooth(method = "lm")

HFC_tl_real_samples <- ggplot(het_fit_real, aes(het_real, tl_alive)) + 
  geom_point() + 
  geom_smooth(method = "lm")

```

## Assess body condition as a fitness variable
```{r}
#Only condition on 2 year old samples####

smbfit_tl_2_data_real

smbfit_mass_data_real <- read_excel("../../raw_data/fitness_data/smbfit_mass.xlsx")

smbfit_tl_mass_real <- merge(smbfit_tl_2_data_real, smbfit_mass_data_real, by = "sample_id")

smbfit_tl_mass_real <- smbfit_tl_mass_real %>%
  mutate(tl_mass_cm = tl_alive/10)

smbfit_tl_mass_real <- smbfit_tl_mass_real %>%
  mutate(condition = mass_g/(tl_mass_cm^3))


het_fit_real_with_condition <- merge(het_data_real, smbfit_tl_mass_real,by = "sample_id")

#Run linear models to test for HFCs
hfc_all_with_condition <- lm(condition ~ het_real, het_fit_real_with_condition)
summary(hfc_all_with_condition) #p = 0.346, r2 = 0.02

HFC_condition_real_samples <- ggplot(hfc_all_with_condition, aes(het_real, condition)) + 
  geom_point() + 
  geom_smooth(method = "lm")


#Condition for ALL samples##
smbfit_raw_data <- read_excel("../../raw_data/master_data/smbfit_master_data_working.xlsx")

smbfit_raw_data_clean <- smbfit_raw_data %>%
  mutate(river = factor(river),
         tl_alive = as.numeric(tl_alive),
         sex = factor(sex),
         hyb_status = factor(hyb_status),
         log_mass = log10(mass_g),
         condition = log_mass/(tl_alive^3))

smbfit_mass_tl_data <- smbfit_raw_data_clean[,-c(2:8,10:11,13:17,19:40)]

smbfit_raw_data_clean_no_outlier <- smbfit_mass_tl_data[-c(13),]

smbfit_raw_data_clean_no_outlier <- smbfit_raw_data_clean_no_outlier %>%
  mutate(sample_id = factor(sample_id))


smbfit_gen_condition_data <- merge(smbfit_two_column,smbfit_raw_data_clean_no_outlier, by = "sample_id")

smbfit_gen_for_condition <- smbfit_gen_condition_data[,-c(30:34)]
smbfit_fit_for_condition <- smbfit_gen_condition_data[,-c(2:29)]

smbfit_gen_for_condition <- column_to_rownames(smbfit_gen_for_condition, "sample_id")

smbfit_genotypes_inbreed_all_condition <- convert_raw(smbfit_gen_for_condition)
check_data(smbfit_genotypes_inbreed_all_condition, num_ind = 115, num_loci = 14)

#heterozygosity per individual
het_all_condition <- sMLH(smbfit_genotypes_inbreed_all_condition)

#variance in heterozygosity
het_all_condition_var<- var(het_all_condition) #0.04

het_all_condition <- as.data.frame(het_all_condition)
het_all_condition <- rownames_to_column(het_all_condition, "sample_id")

het_all_condition <- het_all_condition %>%
  mutate(sample_id = factor(sample_id))

het_fit_all_condition <- cbind(het_all_condition, smbfit_fit_for_condition)
het_fit_all_condition <- het_fit_all_condition[,-c(3)]

het_fit_all_condition <- het_fit_all_condition %>%
  mutate(reg_condition = mass_g/(tl_alive^3))


ggplot(het_fit_all_condition, aes(x = het_all_condition, y= reg_condition)) + 
  geom_point() +
  geom_smooth(method = "lm")

condition_by_het <- lm(reg_condition ~ het_all_condition, het_fit_all_condition)
summary(condition_by_het)
```

```{r}


## Calculate observed heterozygosity for each individual across all loci (proportion of loci that have heterozygous genotype)
```{r}
#calculate observed heterozygosity per locus (give the sample a "1" if heterozygous, "0" if homozygous)
Ho_per_loc <- genetic_diversity(smbfit_msat_data, 
                                stratum = "sample_id", 
                                mode = c("Ho")) 

#Figure out how many loci are represented (have a genotype call) for each individual sample

#Count the number of NAs per individual, because we cannot include in the total number of markers those that did not have a genotype call
    Ho_count_NA <- Ho_per_loc %>%
      mutate(Stratum = factor(Stratum)) %>%
      group_by(Stratum) %>%
      summarize(sum_na = sum(is.na(Ho)))

#Subtract total number of NAs per individual from 14 (which is the total number of starting loci)
    Ho_count_NA$sum_loc <- with(Ho_count_NA, 14 - sum_na)
    
    
#Update the heterozygosity per locus dataset to omit NAs
Ho_per_loc_noNA <- Ho_per_loc %>%
  as.data.frame() %>%
  mutate(Stratum = factor(Stratum), Locus = factor(Locus)) %>%
  drop_na()

#Calculate total number of heterozygous loci per individual
Ho_per_ind <- Ho_per_loc_noNA %>%
  group_by(Stratum) %>%
  summarize(tot_ho = sum(Ho)) 

#Add per-individual heterozygosity to sum of loci dataset
Ho_per_ind <- Ho_per_ind %>%
  left_join(Ho_count_NA, by = "Stratum")


#Calculate per-individual Heterozygosity
Ho_per_ind$Ho <- with(Ho_per_ind, tot_ho/sum_loc)

colnames(Ho_per_ind)[1] <- "sample_id"


#join heterozygosity data with all non-genetic data
smbfit_data_het <- smbfit_data %>%
  left_join(Ho_per_ind, by = "sample_id")




smbfit_data_het$log10_wt <- with(smbfit_data_het, 3.2*log10(tl_alive) - 5.329)
smbfit_data_het$stand_wt <- with(smbfit_data_het, 10^log10_wt)
smbfit_data_het$tl_by_sl <- with(smbfit_data_het, tl_alive/sl)
smbfit_data_het$condition <- with(smbfit_data_het, mass_g/stand_wt)

smbfit_data_het_age2 <- smbfit_data_het %>%
  filter(consensus_age == "2")

ggplot(smbfit_data_het, aes(x = prop_nor, y = condition)) + 
  geom_point() +
  geom_smooth(method = "lm")

ggplot(smbfit_data_het, aes(x = hyb_status, y = )) + 
  geom_boxplot()

summary(lm(condition ~ Ho, smbfit_data_het))
```

