---
title: "SMB_Fitness_Founder_Effects"
author: "Joe Gunn"
date: "6/10/2021"
output: html_document
---
# Aim 6 - Founder effects

## Libraries needed for analysis
```{r setup, include=FALSE}
library(readxl)
library(tidyverse)
library(cowplot)
library(inbreedR)
library(nlme)
library(MuMIn)
library(bbmle)
library(lme4)
library(lmerTest)
library(gstudio)
```

## Read in genetic data.
```{r}
#Read in all Northern Smallmouth Bass data only
gen_data_northern <- read_population("../../raw_data/genotype_data/genotype_files/smbfit_msat_genotypes_northern_only.csv", type = "column", locus.columns = 4:31)

#39 total Northern samples
      #20 in the Northern range
      #19 in the Neosho range

#Data Cleaning:

#Change categorical variables to factors
gen_data_northern$range <- as.factor(gen_data_northern$range)
gen_data_northern$sample_id <- as.factor(gen_data_northern$sample_id)
gen_data_northern$river <- as.factor(gen_data_northern$river)

```

## Measure different genetic diversity metrics across ranges (Northern within the Northern range and Northern within the Neosho range) and at the population level (big sugar creek, and then the two river systems within the Northern range)
```{r}
#Genetic metrics by Ranbge, by locus
A_95_bylocus_range <- genetic_diversity(gen_data_northern, mode = "A95", stratum = "range") # non-rare allele frequency by individual
Ho_bylocus_range <- genetic_diversity(gen_data_northern, mode = "Ho", stratum = "range") 
He_bylocus_range <- genetic_diversity(gen_data_northern,  mode = "He", stratum = "range")
A_bylocus_range <- genetic_diversity(gen_data_northern, mode = "A", stratum = "range") 
Ae_bylocus_range <- genetic_diversity(gen_data_northern, mode = "Ae", stratum = "range")
Fis_bylocus_range <- genetic_diversity(gen_data_northern, mode = "Fis", stratum = "range")

#Average Genetic metrics by Range
A_95_ave_range <- A_95_bylocus_range %>% 
  group_by(Stratum) %>% 
  summarize (mean_A95 = mean(A95)) 

Ho_ave_range <- Ho_bylocus_range %>% 
  group_by(Stratum) %>% 
  summarize(mean_Ho = mean(Ho)) 

He_ave_range <- He_bylocus_range %>% 
  group_by(Stratum) %>% 
  summarize(mean_He = mean(He)) 

A_ave_range <- A_bylocus_range %>%
  group_by(Stratum) %>% 
  summarize (mean_A = mean(A)) 

Ae_ave_range <- Ae_bylocus_range %>% 
  group_by(Stratum) %>% 
  summarize (mean_Ae = mean(Ae)) 

Fis_ave_range <- Fis_bylocus_range %>% 
  group_by(Stratum) %>% 
  summarize (mean_Fis = mean(Fis))


#Genetic metrics by Ranbge, by locus
A_95_bylocus_river <- genetic_diversity(gen_data_northern, mode = "A95", stratum = "river") # non-rare allele frequency by individual
Ho_bylocus_river  <- genetic_diversity(gen_data_northern, mode = "Ho", stratum = "river") 
He_bylocus_river  <- genetic_diversity(gen_data_northern,  mode = "He", stratum = "river")
A_bylocus_river  <- genetic_diversity(gen_data_northern, mode = "A", stratum = "river") 
Ae_bylocus_river  <- genetic_diversity(gen_data_northern, mode = "Ae", stratum = "river")
Fis_bylocus_river  <- genetic_diversity(gen_data_northern, mode = "Fis", stratum = "river")

#Average Genetic metrics by Range
A_95_ave_river  <- A_95_bylocus_river %>% 
  group_by(Stratum) %>% 
  summarize (mean_A95 = mean(A95)) 

Ho_ave_river  <- Ho_bylocus_river %>% 
  group_by(Stratum) %>% 
  summarize(mean_Ho = mean(Ho)) 

He_ave_river <- He_bylocus_river %>% 
  group_by(Stratum) %>% 
  summarize(mean_He = mean(He)) 

A_ave_river <- A_bylocus_river %>%
  group_by(Stratum) %>% 
  summarize (mean_A = mean(A)) 

Ae_ave_river <- Ae_bylocus_river %>% 
  group_by(Stratum) %>% 
  summarize (mean_Ae = mean(Ae)) 

Fis_ave_river <- Fis_bylocus_river %>% 
  group_by(Stratum) %>% 
  summarize (mean_Fis = mean(Fis)) 
```

## Gather up all data tables and convert into one usable table for the ms
```{r}
A_95_bylocus_range <- A_95_bylocus_range %>%
  mutate(Stratum = factor(Stratum),
         Locus = factor(Locus),
         A95 = as.numeric(A95))

Ho_bylocus_range <- Ho_bylocus_range %>%
  mutate(Stratum = factor(Stratum),
         Locus = factor(Locus),
         Ho = as.numeric(Ho))

He_bylocus_range <- He_bylocus_range %>%
  mutate(Stratum = factor(Stratum),
         Locus = factor(Locus),
         He = as.numeric(He))

A_bylocus_range <- A_bylocus_range %>%
  mutate(Stratum = factor(Stratum),
         Locus = factor(Locus),
         A = as.numeric(A))

Ae_bylocus_range <- Ae_bylocus_range %>%
  mutate(Stratum = factor(Stratum),
         Locus = factor(Locus),
         Ae = as.numeric(Ae))

Fis_bylocus_range <- Fis_bylocus_range %>%
  mutate(Stratum = factor(Stratum),
         Locus = factor(Locus),
         Fis = as.numeric(Fis))

all_gen_metrics_by_range <- cbind(A_bylocus_range, 
      A_95_bylocus_range, 
      Ae_bylocus_range, 
      Ho_bylocus_range, 
      He_bylocus_range,
      Fis_bylocus_range)

all_gen_metrics_by_range <- all_gen_metrics_by_range[,-c(4:5,7:8,10:11,13:14,16:17)]

write.table(all_gen_metrics_by_range,"~/Desktop/Grad_School_Stuff/Research/Projects/Smallmouth_Bass_Fitness/tables_and_figures/tables_being_built/all_gen_metrics_by_range", sep="\t")

A_95_bylocus_river <- A_95_bylocus_river %>%
  mutate(Stratum = factor(Stratum),
         Locus = factor(Locus),
         A95 = as.numeric(A95))

Ho_bylocus_river <- Ho_bylocus_river %>%
  mutate(Stratum = factor(Stratum),
         Locus = factor(Locus),
         Ho = as.numeric(Ho))

He_bylocus_river <- He_bylocus_river %>%
  mutate(Stratum = factor(Stratum),
         Locus = factor(Locus),
         He = as.numeric(He))

A_bylocus_river <- A_bylocus_river %>%
  mutate(Stratum = factor(Stratum),
         Locus = factor(Locus),
         A = as.numeric(A))

Ae_bylocus_river <- Ae_bylocus_river %>%
  mutate(Stratum = factor(Stratum),
         Locus = factor(Locus),
         Ae = as.numeric(Ae))

Fis_bylocus_river <- Fis_bylocus_river %>%
  mutate(Stratum = factor(Stratum),
         Locus = factor(Locus),
         Fis = as.numeric(Fis))

all_gen_metrics_by_river <- cbind(A_bylocus_river, 
      A_95_bylocus_river, 
      Ae_bylocus_river, 
      Ho_bylocus_river, 
      He_bylocus_river,
      Fis_bylocus_river)

all_gen_metrics_by_river <- all_gen_metrics_by_river[,-c(4:5,7:8,10:11,13:14,16:17)]

write.table(all_gen_metrics_by_river,"~/Desktop/Grad_School_Stuff/Research/Projects/Smallmouth_Bass_Fitness/tables_and_figures/tables_being_built/all_gen_metrics_by_river", sep="\t")
```

## Plotting by range
```{r}

#levels(A_95_bylocus_range$Stratum) <- c("Neosho","Northern")

#A95_bylocus_range_plot <- ggplot(A_95_bylocus_range, aes(x = Stratum, y = A95)) +
#  geom_boxplot(show.legend = F, outlier.shape = NA, alpha = 0.3, fill = "grey") +
 # geom_point(position = position_jitter(width = 0.1), size = 3, color = "black", pch = 21, show.legend = F, fill = "grey") +
  #theme_set(theme_cowplot(12)) +
  #labs(x = "Subspecies Range", y = "A95") +
  #scale_fill_manual(values = c("grey","grey")) +
  #theme(axis.title = element_text(size = 20)) +
  #theme(axis.text = element_text(size = 15)) +
  #ylab(expression(~A[95])) +
  #theme(axis.title.x = element_text(margin = margin(t = 10))) +
  #theme(panel.border = element_rect(colour = "black", fill=NA, size=1)) +
  #theme(axis.text.x = element_blank()) + 
  #scale_y_continuous(labels = number_format(accuracy = 0.01,
                              #   decimal.mark = '.'))
  
levels(Ho_bylocus_range$Stratum) <- c("Neosho","Northern")

Ho_bylocus_range_plot <- ggplot(Ho_bylocus_range, aes(x = Stratum, y = Ho)) +
  geom_boxplot(show.legend = F, outlier.shape = NA, alpha = 0.3, fill = "grey") +
  geom_point(position = position_jitter(width = 0.1), size = 3, color = "black", pch = 21, show.legend = F, fill = "grey") +
  theme_set(theme_cowplot(12)) +
  labs(x = "Subspecies Range", y = "Ho") +
  scale_fill_manual(values = c("grey","grey")) +
  theme(axis.title = element_text(size = 20)) +
  theme(axis.text = element_text(size = 15)) +
  ylab(expression(~H[O])) +
  theme(axis.title.x = element_text(margin = margin(t = 10))) +
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1))  +
  theme(axis.text.x = element_blank()) + 
  scale_y_continuous(labels = number_format(accuracy = 0.01,
                                 decimal.mark = '.'))
  
levels(He_bylocus_range$Stratum) <- c("Neosho","Northern")

He_bylocus_range_plot <- ggplot(He_bylocus_range, aes(x = Stratum, y = He)) +
  geom_boxplot(show.legend = F, outlier.shape = NA, alpha = 0.3, fill = "grey") +
  geom_point(position = position_jitter(width = 0.1), size = 3, color = "black", pch = 21, show.legend = F, fill = "grey") +
  theme_set(theme_cowplot(12)) +
  labs(x = "Subspecies Range", y = "He") +
  scale_fill_manual(values = c("grey","grey")) +
  theme(axis.title = element_text(size = 20)) +
  theme(axis.text = element_text(size = 15)) +
  ylab(expression(~H[E])) +
  theme(axis.title.x = element_text(margin = margin(t = 10))) +
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1))  +
  scale_y_continuous(labels = number_format(accuracy = 0.01,
                                 decimal.mark = '.'))
  
levels(A_bylocus_range$Stratum) <- c("Neosho","Northern")

A_bylocus_range_plot <- ggplot(A_bylocus_range, aes(x = Stratum, y = A)) +
  geom_boxplot(show.legend = F, outlier.shape = NA, alpha = 0.3, fill = "grey") +
  geom_point(position = position_jitter(width = 0.1), size = 3, color = "black", pch = 21, show.legend = F, fill = "grey") +
  theme_set(theme_cowplot(12)) +
  labs(x = "Subspecies Range", y = "A") +
  scale_fill_manual(values = c("grey","grey")) +
  theme(axis.title = element_text(size = 20)) +
  theme(axis.text = element_text(size = 15)) +
  theme(axis.title.x = element_text(margin = margin(t = 10))) +
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1))  +
  theme(axis.text.x = element_blank()) + 
  scale_y_continuous(labels = number_format(accuracy = 0.01,
                                 decimal.mark = '.'))

#levels(Ae_bylocus_range$Stratum) <- c("Neosho","Northern")

#Ae_bylocus_range_plot <- ggplot(Ae_bylocus_range, aes(x = Stratum, y = Ae)) +
 # geom_boxplot(show.legend = F, outlier.shape = NA, alpha = 0.3, fill = "grey") +
  #geom_point(position = position_jitter(width = 0.1), size = 3, color = "black", pch = 21, show.legend = F, fill = "grey") +
  #theme_set(theme_cowplot(12)) +
  #labs(x = "Subspecies Range", y = "Ae") +
  #scale_fill_manual(values = c("grey","grey")) +
  #theme(axis.title = element_text(size = 20)) +
  #theme(axis.text = element_text(size = 15)) +
  #ylab(expression(~A[E])) +
  #theme(axis.title.x = element_text(margin = margin(t = 10))) +
  #theme(panel.border = element_rect(colour = "black", fill=NA, size=1))  +
  #theme(axis.text.x = element_blank()) + 
  #scale_y_continuous(labels = number_format(accuracy = 0.01,
                              #   decimal.mark = '.'))

levels(Fis_bylocus_range$Stratum) <- c("Neosho","Northern")

Fis_bylocus_range_plot <- ggplot(Fis_bylocus_range, aes(x = Stratum, y = Fis)) +
  geom_boxplot(show.legend = F, outlier.shape = NA, alpha = 0.3, fill = "grey") +
  geom_point(position = position_jitter(width = 0.1), size = 3, color = "black", pch = 21, show.legend = F, fill = "grey") +
  theme_set(theme_cowplot(12)) +
  labs(x = "Subspecies Range", y = "Fis") +
  scale_fill_manual(values = c("grey","grey")) +
  theme(axis.title = element_text(size = 20)) +
  theme(axis.text = element_text(size = 15)) +
  ylab(expression(~F[IS])) +
  theme(axis.title.x = element_text(margin = margin(t = 10))) +
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1))

pdf("/Users/joegunn/Desktop/Grad_School_Stuff/Research/Projects/Smallmouth_Bass_Fitness/visualization/founder_effect_plots/founder_effect_by_range.pdf", width = 12, height = 10)

plot_grid(A_bylocus_range_plot,
          Ho_bylocus_range_plot,
          He_bylocus_range_plot,
          Fis_bylocus_range_plot,
          nrow = 3,
          labels = c("a","b","c","d"),
          label_size = 25,
          align = "v")

dev.off()

##Run linear models 

A_bylocus_range_lm <- lm(A ~ Stratum, A_bylocus_range)
summary(A_bylocus_range_lm)

Ho_bylocus_range_lm <- lm(Ho ~ Stratum, Ho_bylocus_range)
summary(Ho_bylocus_range_lm)

He_bylocus_range_lm <- lm(He ~ Stratum, He_bylocus_range)
summary(He_bylocus_range_lm)

Fis_bylocus_range_lm <- lm(Fis ~ Stratum, Fis_bylocus_range)
summary(Fis_bylocus_range_lm )
```

## Plotting by River
```{r}
#levels(A_95_bylocus_river$Stratum) <- c("Big Sugar Creek","Elk River", "Tablerock Lake","White River")

#A95_bylocus_river_plot <- ggplot(A_95_bylocus_river, aes(x = Stratum, y = A95)) +
 # geom_boxplot(show.legend = F, outlier.shape = NA, alpha = 0.3, fill = "grey") +
  #geom_point(position = position_jitter(width = 0.1), size = 3, color = "black", pch = 21, show.legend = F, fill = "grey") +
  #theme_set(theme_cowplot(12)) +
  #labs(x = "River", y = "A95") +
  #scale_fill_manual(values = c("grey","grey")) +
  #theme(axis.title = element_text(size = 20)) +
  #theme(axis.text = element_text(size = 15)) +
  #ylab(expression(~A[95])) +
  #theme(axis.title.x = element_text(margin = margin(t = 10))) +
  #theme(panel.border = element_rect(colour = "black", fill=NA, size=1)) + 
  #theme(axis.title.x = element_blank()) +
  #theme(axis.text.x = element_blank()) + 
  #scale_y_continuous(labels = number_format(accuracy = 0.01,
    #                             decimal.mark = '.'))
  
levels(Ho_bylocus_river$Stratum) <- c("Big Sugar Creek","Elk River", "Tablerock Lake","White River")

Ho_bylocus_river_plot <- ggplot(Ho_bylocus_river, aes(x = Stratum, y = Ho)) +
  geom_boxplot(show.legend = F, outlier.shape = NA, alpha = 0.3, fill = "grey") +
  geom_point(position = position_jitter(width = 0.1), size = 3, color = "black", pch = 21, show.legend = F, fill = "grey") +
  theme_set(theme_cowplot(12)) +
  labs(x = "River", y = "Ho") +
  scale_fill_manual(values = c("grey","grey")) +
  theme(axis.title = element_text(size = 20)) +
  theme(axis.text = element_text(size = 15)) +
  ylab(expression(~H[O])) +
  theme(axis.title.x = element_text(margin = margin(t = 10))) +
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1)) + 
  theme(axis.text.x = element_blank())
  
levels(He_bylocus_river$Stratum) <- c("Big Sugar Creek","Elk River", "Tablerock Lake","White River")

He_bylocus_river_plot <- ggplot(He_bylocus_river, aes(x = Stratum, y = He)) +
  geom_boxplot(show.legend = F, outlier.shape = NA, alpha = 0.3, fill = "grey") +
  geom_point(position = position_jitter(width = 0.1), size = 3, color = "black", pch = 21, show.legend = F, fill = "grey") +
  theme_set(theme_cowplot(12)) +
  labs(x = "River", y = "He") +
  scale_fill_manual(values = c("grey","grey")) +
  theme(axis.title = element_text(size = 20)) +
  theme(axis.text = element_text(size = 15)) +
  ylab(expression(~H[E])) +
  theme(axis.title.x = element_text(margin = margin(t = 10))) +
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1)) 
  
levels(A_bylocus_river$Stratum) <- c("Big Sugar Creek","Elk River", "Tablerock Lake","White River")

A_bylocus_river_plot <- ggplot(A_bylocus_river, aes(x = Stratum, y = A)) +
  geom_boxplot(show.legend = F, outlier.shape = NA, alpha = 0.3, fill = "grey") +
  geom_point(position = position_jitter(width = 0.1), size = 3, color = "black", pch = 21, show.legend = F, fill = "grey") +
  theme_set(theme_cowplot(12)) +
  labs(x = "River", y = "A") +
  scale_fill_manual(values = c("grey","grey")) +
  theme(axis.title = element_text(size = 20)) +
  theme(axis.text = element_text(size = 15)) +
  theme(axis.title.x = element_text(margin = margin(t = 10))) +
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1)) + 
  theme(axis.text.x = element_blank()) + 
  scale_y_continuous(labels = number_format(accuracy = 0.01,
                                 decimal.mark = '.'))
  
#levels(Ae_bylocus_river$Stratum) <- c("Big Sugar Creek","Elk River", "Tablerock Lake","White River")

#Ae_bylocus_river_plot <- ggplot(Ae_bylocus_river, aes(x = Stratum, y = Ae)) +
 # geom_boxplot(show.legend = F, outlier.shape = NA, alpha = 0.3, fill = "grey") +
  #geom_point(position = position_jitter(width = 0.1), size = 3, color = "black", pch = 21, show.legend = F, fill = "grey") +
  #theme_set(theme_cowplot(12)) +
  #labs(x = "River", y = "Ae") +
  #scale_fill_manual(values = c("grey","grey")) +
  #theme(axis.title = element_text(size = 20)) +
  #theme(axis.text = element_text(size = 15)) +
  #ylab(expression(~A[E])) +
  #theme(axis.title.x = element_text(margin = margin(t = 10))) +
  #theme(panel.border = element_rect(colour = "black", fill=NA, size=1)) + 
  #theme(axis.title.x = element_blank()) +
  #theme(axis.text.x = element_blank()) + 
  #scale_y_continuous(labels = number_format(accuracy = 0.01,
   #                              decimal.mark = '.'))
  
levels(Fis_bylocus_river$Stratum) <- c("Big Sugar Creek","Elk River", "Tablerock Lake","White River")

Fis_bylocus_river_plot <- ggplot(Fis_bylocus_river, aes(x = Stratum, y = Fis)) +
  geom_boxplot(show.legend = F, outlier.shape = NA, alpha = 0.3, fill = "grey") +
  geom_point(position = position_jitter(width = 0.1), size = 3, color = "black", pch = 21, show.legend = F, fill = "grey") +
  theme_set(theme_cowplot(12)) +
  labs(x = "River", y = "Fis") +
  scale_fill_manual(values = c("grey","grey")) +
  theme(axis.title = element_text(size = 20)) +
  theme(axis.text = element_text(size = 15)) +
  ylab(expression(~F[IS])) +
  theme(axis.title.x = element_text(margin = margin(t = 10))) +
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1)) + 
  scale_y_continuous(labels = number_format(accuracy = 0.01,
                                 decimal.mark = '.'))
  
pdf("/Users/joegunn/Desktop/Grad_School_Stuff/Research/Projects/Smallmouth_Bass_Fitness/visualization/founder_effect_plots/founder_effect_by_river.pdf", width = 13, height = 10)

plot_grid(A_bylocus_river_plot,
          Ho_bylocus_river_plot,
          He_bylocus_river_plot,
          Fis_bylocus_river_plot,
          nrow = 3,
          labels = c("a","b","c","d"),
          label_size = 25,
          align = "v")

dev.off()

##Run linear models 
A_bylocus_river_lm <- lm(A ~ Stratum, A_bylocus_river)
summary(A_bylocus_river_lm)

Ho_bylocus_river_lm <- lm(Ho ~ Stratum, Ho_bylocus_river)
summary(Ho_bylocus_river_lm)

He_bylocus_river_lm <- lm(He ~ Stratum, He_bylocus_river)
summary(He_bylocus_river_lm)

Fis_bylocus_river_lm <- lm(Fis ~ Stratum, Fis_bylocus_river)
summary(Fis_bylocus_river_lm )

```


