---
title: "SMB_Fitness_HFC"
author: "Joe Gunn"
date: "6/6/2021"
output: html_document
---
# Aim 5 - Heterozygosity-fitness correlations

## Read in libraries needed for analysis
```{r, include=FALSE}
library(readxl)
library(tidyverse)
library(cowplot)
library(inbreedR)
library(nlme)
library(MuMIn)
library(bbmle)
library(lme4)
library(lmerTest)
library(multcomp)
library(scales)
```

## Read in and organize fitness data
```{r}

smbfit_raw_data <- read_excel("../../raw_data/master_data/smbfit_master_data_working.xlsx")

smbfit_raw_data_clean <- smbfit_raw_data %>%
  mutate(river = factor(river),
         tl_alive = as.numeric(tl_alive),
         tl_alive_cm = tl_alive/10,
         sex = factor(sex),
         hyb_status = factor(hyb_status),
         log_mass = log10(mass_g),
         pure_admix = factor(pure_admix))

smbfit_raw_data_clean <- smbfit_raw_data_clean %>%
  mutate(condition = mass_g/(tl_alive_cm^3))

smbfit_mass_tl_data <- smbfit_raw_data_clean[,-c(2:4,6:8,10:11,13:17,19:23,25:33,36:37,39:41)]

smbfit_raw_data_clean_no_outlier <- smbfit_mass_tl_data[-c(13),]

fitness_data <- smbfit_raw_data_clean_no_outlier %>%
  mutate(sample_id = factor(sample_id)) %>%
  mutate(age_factor = factor(consensus_age))

fitness_data_4yo <- fitness_data %>%
  filter(consensus_age < 5) # 105 samples total that are less than 4 yo

fitness_data_4yo_bsug <- fitness_data_4yo %>%
  filter(river == "BSUG") #40

fitness_data_4yo_elk <- fitness_data_4yo %>%
  filter(river == "ELK") #65
```

## Assess body condition as a possible proxy for fitness, including how it is correlated with age
```{r}
##GLOBAL

#condition is calculated as mass divided by total length (cm) cubed, so it deals with both mass and length
 
#How does mass scale with length
global_mass_tl <- ggplot(fitness_data_4yo, aes(x = tl_alive, y = mass_g)) +
  geom_point(size = 2.5) +
  geom_smooth(method = "lm", se = F, color = "black") +
  theme_set(theme_cowplot(12)) +
  labs(x = "Total Length (mm)", y = "Mass (g)") +
  theme(axis.title = element_text(size = 20)) +
  theme(axis.text = element_text(size = 15)) +
  scale_x_continuous(expand = c(0, 0), breaks = seq(0,400,50)) + 
  scale_y_continuous(expand = c(0, 0)) +
  expand_limits(y = 700, x = 400) +
  theme(axis.title.x = element_text(margin = margin(t = 10))) +
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1)) 

  
mass_by_tl_corr <- lm(mass_g ~ tl_alive, fitness_data_4yo)
summary(mass_by_tl_corr) #r2 = 0.937, p <0.001

#Is condition correlated with age?
global_age_condition <- ggplot(fitness_data_4yo, aes(x = consensus_age, y = condition)) +
  geom_point(size = 2.5, alpha = 0.5, position = position_jitter(width = 0.1)) +
  geom_smooth(method = "lm", se = F, color = "black") +
  theme_set(theme_cowplot(12)) +
  labs(x = "Age (years)", y = "Condition (g/cm3)") +
  theme(axis.title = element_text(size = 20)) +
  theme(axis.text = element_text(size = 15)) +
  scale_x_continuous(expand = c(0, 0), breaks = seq(0,4,1)) + 
  scale_y_continuous(expand = c(0, 0)) +
  expand_limits(y = 0.01, x = 4) +
  ylab(expression(Condition~(g/cm^{"3"}))) + 
  theme(axis.title.x = element_text(margin = margin(t = 10))) +
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1)) 


condition_by_age_corr <- lm(condition ~ consensus_age, fitness_data_4yo)
summary(condition_by_age_corr) #r2 = 0.009, p = 0.346

#Is condition normally distributed?
global_condition_norm <- ggplot(fitness_data_4yo, aes(condition)) +
  geom_histogram(fill = "grey", color = "black") +
  theme_set(theme_cowplot(12)) +
  labs(x = "Condition (g/cm3)", y = "Frequency") +
  theme(axis.title = element_text(size = 20)) +
  theme(axis.text = element_text(size = 15)) +
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1))  +
  xlab(expression(Condition~(g/cm^{"3"}))) 


shapiro.test(fitness_data_4yo$condition)
#p = 0.4304, W = 0.969


##BIG SUGAR CREEK

#condition is calculated as mass divided by total length (cm) cubed, so it deals with both mass and length
 
#How does mass scale with length
bsug_mass_tl <- ggplot(fitness_data_4yo_bsug, aes(x = tl_alive, y = mass_g)) +
  geom_point(size = 2.5) +
  geom_smooth(method = "lm", se = F, color = "black") +
  theme_set(theme_cowplot(12)) +
  labs(x = "Total Length (mm)", y = "Mass (g)") +
  theme(axis.title = element_text(size = 20)) +
  theme(axis.text = element_text(size = 15)) +
  scale_x_continuous(expand = c(0, 0), breaks = seq(0,350,50)) + 
  scale_y_continuous(expand = c(0, 0)) +
  expand_limits(y = 600, x = 350) +
  theme(axis.title.x = element_text(margin = margin(t = 10))) +
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1)) +
  theme(axis.title.y = element_blank())

  
mass_by_tl_corr_bsug <- lm(mass_g ~ tl_alive, fitness_data_4yo_bsug)
summary(mass_by_tl_corr_bsug) #r2 = 0.94, p <0.001

#Is condition correlated with age?
bsug_age_condition <- ggplot(fitness_data_4yo_bsug, aes(x = consensus_age, y = condition)) +
  geom_point(size = 2.5, alpha = 0.5, position = position_jitter(width = 0.1)) +
  geom_smooth(method = "lm", se = F, color = "black") +
  theme_set(theme_cowplot(12)) +
  labs(x = "Age (years)", y = "Condition (g/cm3)") +
  theme(axis.title = element_text(size = 20)) +
  theme(axis.text = element_text(size = 15)) +
  scale_x_continuous(expand = c(0, 0), breaks = seq(0,4,1)) + 
  scale_y_continuous(expand = c(0, 0)) +
  expand_limits(y = 0.01, x = 4) +
  ylab(expression(Condition~(g/cm^{"3"}))) + 
  theme(axis.title.x = element_text(margin = margin(t = 10))) +
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1)) +
  theme(axis.title.y = element_blank())


condition_by_age_corr_bsug <- lm(condition ~ consensus_age, fitness_data_4yo_bsug)
summary(condition_by_age_corr_bsug) #r2 = 0.05, p = 0.147

#Is condition normally distributed?
bsug_condition_norm <- ggplot(fitness_data_4yo_bsug, aes(condition)) +
  geom_histogram(fill = "grey", color = "black") +
  theme_set(theme_cowplot(12)) +
  labs(x = "Condition (g/cm3)", y = "Frequency") +
  theme(axis.title = element_text(size = 20)) +
  theme(axis.text = element_text(size = 15)) +
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1)) +
  theme(axis.title.y = element_blank())  +
  xlab(expression(Condition~(g/cm^{"3"})))
 


condition_norm_bsug <- shapiro.test(fitness_data_4yo_bsug$condition)
#p = 0.117, W = 0.955


##ELK RIVER

#condition is calculated as mass divided by total length (cm) cubed, so it deals with both mass and length
 
#How does mass scale with length
elk_mass_tl <- ggplot(fitness_data_4yo_elk, aes(x = tl_alive, y = mass_g)) +
  geom_point(size = 2.5) +
  geom_smooth(method = "lm", se = F, color = "black") +
  theme_set(theme_cowplot(12)) +
  labs(x = "Total Length (mm)", y = "Mass (g)") +
  theme(axis.title = element_text(size = 20)) +
  theme(axis.text = element_text(size = 15)) +
  scale_x_continuous(expand = c(0, 0), breaks = seq(0,350,50)) + 
  scale_y_continuous(expand = c(0, 0)) +
  expand_limits(y = 600, x = 350) +
  theme(axis.title.x = element_text(margin = margin(t = 10))) +
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1)) +
  theme(axis.title.y = element_blank()) 

  
mass_by_tl_corr_elk <- lm(mass_g ~ tl_alive, fitness_data_4yo_elk)
summary(mass_by_tl_corr_elk) #r2 = 0.94, p <0.001

#Is condition correlated with age?
elk_age_condition <- ggplot(fitness_data_4yo_elk, aes(x = consensus_age, y = condition)) +
  geom_point(size = 2.5, alpha = 0.5, position = position_jitter(width = 0.1)) +
  geom_smooth(method = "lm", se = F, color = "black") +
  theme_set(theme_cowplot(12)) +
  labs(x = "Age (years)", y = "Condition (g/cm3)") +
  theme(axis.title = element_text(size = 20)) +
  theme(axis.text = element_text(size = 15)) +
  scale_x_continuous(expand = c(0, 0), breaks = seq(0,4,1)) + 
  scale_y_continuous(expand = c(0, 0)) +
  expand_limits(y = 0.01, x = 4) +
  ylab(expression(Condition~(g/cm^{"3"}))) + 
  theme(axis.title.x = element_text(margin = margin(t = 10))) +
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1)) +
  theme(axis.title.y = element_blank()) 


condition_by_age_corr_elk <- lm(condition ~ consensus_age, fitness_data_4yo_elk)
summary(condition_by_age_corr_elk) #r2 = 0.001, p = 0.781

#Is condition normally distributed?
elk_condition_norm <- ggplot(fitness_data_4yo_elk, aes(condition)) +
  geom_histogram(fill = "grey", color = "black") +
  theme_set(theme_cowplot(12)) +
  labs(x = "Condition (g/cm^3)", y = "Frequency") +
  theme(axis.title = element_text(size = 20)) +
  theme(axis.text = element_text(size = 15)) +
  xlab(expression(Condition~(g/cm^{"3"}))) + 
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1)) +
  theme(axis.title.y = element_blank()) 

condition_norm_elk <- shapiro.test(fitness_data_4yo_elk$condition)
#p = 0.181, W = 0.973

pdf("/Users/joegunn/Desktop/Grad_School_Stuff/Research/Projects/Smallmouth_Bass_Fitness/visualization/hfc_plots/condition_check_plots.pdf", width = 13, height = 12)

plot_grid(global_mass_tl, 
          bsug_mass_tl,
          elk_mass_tl,
          global_age_condition, 
          bsug_age_condition,
          elk_age_condition,
          global_condition_norm,
          bsug_condition_norm,
          elk_condition_norm,
          nrow = 3,
          labels = c("a","b","c","d","e","f","g","h","i"),
          label_size = 25,
          label_y = 1.04,
          align = "v")

dev.off()
```

## Read in genetic data, and convert to inbreedR format for the global dataset, the big sugar dataset, and the elk river dataset
```{r}
# Read in genetic data with inbreed R
gen_data <- read_csv("../../raw_data/genotype_data/genotype_files/smbfit_msat_genotypes_noHSYC.csv")

gen_data_all_with_fitness <- merge(fitness_data_4yo, gen_data, by = "sample_id")

gen_data_all <- gen_data_all_with_fitness[,-c(2:13)]
gen_data_all <- column_to_rownames(gen_data_all, "sample_id")

gen_data_inbreedr <- convert_raw(gen_data_all)
check_data(gen_data_inbreedr)

gen_data_bsug_with_fitness <- gen_data_all_with_fitness %>%
  filter(river == "BSUG")

gen_data_elk_with_fitness <- gen_data_all_with_fitness %>%
  filter(river == "ELK")

gen_data_bsug_with_fitness <- column_to_rownames(gen_data_bsug_with_fitness, "sample_id")
gen_data_elk_with_fitness <- column_to_rownames(gen_data_elk_with_fitness, "sample_id")

gen_data_bsug <- gen_data_bsug_with_fitness[,-c(1:12)]
gen_data_elk <- gen_data_elk_with_fitness[,-c(1:12)]

gen_data_bsug_inbreedr <- convert_raw(gen_data_bsug)
check_data(gen_data_bsug_inbreedr)

gen_data_elk_inbreedr <- convert_raw(gen_data_elk)
check_data(gen_data_elk_inbreedr)
```

## Calcualte g2 coefficients for each dataset (g2 measures identity disequilibrium, which is a measure of how correlated heterozygosity is and tells you whether you have high power of detecting general effects of inbreeding across the genome (if high correlation among loci, then we assume that the rest of the genome is probably mostly heterozygous))
```{r}
g2_global <- g2_microsats(gen_data_inbreedr, nperm = 1000, nboot = 1000, CI = 0.95)
#p = 0.04, se = 0.006, 2.5% ci = -0.001, 97.5% ci = 0.233, g2 = 0.010

g2_bsug <- g2_microsats(gen_data_bsug_inbreedr, nperm = 1000, nboot = 1000, CI = 0.95)
#p = 0.377, se = 0.009, 2.5% ci = -0.014, 97.5% ci = 0.024, g2 = 0.002

g2_elk <- g2_microsats(gen_data_elk_inbreedr, nperm = 1000, nboot = 1000, CI = 0.95)
#p = 0.025, se = 0.008, 2.5% ci = 0.0005, 97.5% ci = 0.030, g2 = 0.015
```

## Get heterozygosity measures per individual in each dataset
```{r}

het_global <- as.data.frame(sMLH(gen_data_inbreedr))
het_global <- rownames_to_column(het_global, "sample_id")
het_global <- het_global %>%
  mutate(sample_id = factor(sample_id))
colnames(het_global) <- c("sample_id","het")

het_bsug <- as.data.frame(sMLH(gen_data_bsug_inbreedr))
het_bsug <- rownames_to_column(het_bsug, "sample_id")
het_bsug <- het_bsug %>%
  mutate(sample_id = factor(sample_id))
colnames(het_bsug) <- c("sample_id","het")

het_elk <- as.data.frame(sMLH(gen_data_elk_inbreedr))
het_elk <- rownames_to_column(het_elk, "sample_id")
het_elk <- het_elk %>%
  mutate(sample_id = factor(sample_id))
colnames(het_elk) <- c("sample_id","het")
 
global_het_fitness <- merge(het_global, fitness_data_4yo, by = "sample_id")
bsug_het_fitness <- merge(het_bsug, fitness_data_4yo_bsug, by = "sample_id")
elk_het_fitness <- merge(het_elk, fitness_data_4yo_elk, by = "sample_id")

#plot condition by heterozygosity
global_het_fitness_plot <- ggplot(global_het_fitness, aes(x = het,y = condition)) + 
  geom_point(size = 2.5) +
  geom_smooth(method = "lm", se = F, color = "black") +
  theme_set(theme_cowplot(12)) +
  labs(x = "Multilocus heterozygosity", y = "Body condition (g/cm3)") +
  theme(axis.title = element_text(size = 20)) +
  theme(axis.text = element_text(size = 15)) +
  scale_x_continuous(expand = c(0, 0), breaks = seq(0,1.5,0.1)) + 
  scale_y_continuous(expand = c(0, 0)) +
  expand_limits(y = 0.01, x = 1.4) +
  ylab(expression(Condition~(g/cm^{"3"}))) + 
  theme(axis.title.x = element_text(margin = margin(t = 10))) +
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1)) +
  theme(axis.title.x = element_blank())

global_het_fitness <- global_het_fitness[-c(105),]

global_het_fitness_lme <- lme(condition ~ het, random = ~1|sex, global_het_fitness)
summary(global_het_fitness_lme)
anova.lme(global_het_fitness_lme)
r.squaredGLMM(global_het_fitness_lme)
#p = 0.032, F = 4.75, R2 =0.035

global_het_fitness_lm <- lm(condition ~ het, global_het_fitness)
summary(global_het_fitness_lm)

bsug_het_fitness_plot <- ggplot(bsug_het_fitness, aes(x = het, y = condition)) + 
  geom_point(size = 2.5) +
  geom_smooth(method = "lm", se = F, color = "black") +
  theme_set(theme_cowplot(12)) +
  labs(x = "Multilocus heterozygosity", y = "Body condition (g/cm3)") +
  theme(axis.title = element_text(size = 20)) +
  theme(axis.text = element_text(size = 15)) +
  scale_x_continuous(expand = c(0, 0), breaks = seq(0,1.5,0.1)) + 
  scale_y_continuous(expand = c(0, 0)) +
  expand_limits(y = 0.01, x = 1.4) +
  ylab(expression(Condition~(g/cm^{"3"}))) + 
  theme(axis.title.x = element_text(margin = margin(t = 10))) +
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1)) +
  theme(axis.title.x = element_blank())

bsug_het_fitness_lme <- lme(condition ~ het, random = ~1|sex, bsug_het_fitness)
anova.lme(bsug_het_fitness_lme)
r.squaredGLMM(bsug_het_fitness_lme)
#p = 0.206, F = 1.65


elk_het_fitness_plot <- ggplot(elk_het_fitness, aes(x = het, y = condition)) + 
  geom_point(size = 2.5) +
  geom_smooth(method = "lm", se = F, color = "black") +
  theme_set(theme_cowplot(12)) +
  labs(x = "Standardized multilocus heterozygosity", y = "Body condition (g/cm3)") +
  theme(axis.title = element_text(size = 20)) +
  theme(axis.text = element_text(size = 15)) +
  scale_x_continuous(expand = c(0, 0), breaks = seq(0,1.5,0.1)) + 
  scale_y_continuous(expand = c(0, 0)) +
  expand_limits(y = 0.01, x = 1.4) +
  ylab(expression(Condition~(g/cm^{"3"}))) + 
  theme(axis.title.x = element_text(margin = margin(t = 10))) +
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1))
 
elk_het_fitness <- elk_het_fitness[-c(65),]

elk_het_fitness_lme <- lme(condition ~ het, random = ~1|sex, elk_het_fitness)
anova.lme(elk_het_fitness_lme)
r.squaredGLMM(elk_het_fitness_lme)
#p = 0.07, F = 3.45

pdf("/Users/joegunn/Desktop/Grad_School_Stuff/Research/Projects/Smallmouth_Bass_Fitness/visualization/hfc_plots/hfc_plots.pdf", width = 7, height = 15)

plot_grid(global_het_fitness_plot,
          bsug_het_fitness_plot,
          elk_het_fitness_plot,
          nrow = 3)

dev.off()


global_het_fitness_by_hybstatus_plot <- ggplot() + 
  geom_point(data = global_het_fitness_admix, size = 3, aes(x = het, y = condition, group = hyb_status, fill = hyb_status, shape = hyb_status), color = "black", pch = 21, show.legend = T) +
  geom_smooth(data = global_het_fitness_admix, aes(x = het, y = condition, color = hyb_status), show.legend = T, method = "lm", se=F, fullrange = T) +
  geom_point(data = global_het_fitness_neosho, size = 3, aes(x = het, y = condition, group = hyb_status, fill = hyb_status, shape = hyb_status), color = "black", pch = 22, show.legend = T) +
  geom_smooth(data = global_het_fitness_neosho, aes(x = het, y = condition, color = hyb_status), show.legend = T, method = "lm", se=F, fullrange = T) +
  geom_point(data = global_het_fitness_northern, size = 3, aes(x = het, y = condition, group = hyb_status, fill = hyb_status, shape = hyb_status), color = "black", pch = 24, show.legend = T) +
  geom_smooth(data = global_het_fitness_northern, aes(x = het, y = condition, color = hyb_status), show.legend = T, method = "lm", se=F, fullrange = T) +
  theme_set(theme_cowplot(12)) +
  labs(x = "Multilocus heterozygosity", y = "Body condition (g/cm3)", fill = "Admixture Status", color = "Admixture Status") +
  theme(axis.title = element_text(size = 20)) +
  theme(axis.text = element_text(size = 15)) +
  scale_fill_manual(values = c("mediumpurple","deepskyblue2","deeppink2")) +
  scale_color_manual(values = c("mediumpurple","deepskyblue2","deeppink2")) +
  scale_shape_manual(values = c("circle","square","triangle")) +
  scale_x_continuous(expand = c(0, 0), breaks = seq(0,1.5,0.1)) + 
  scale_y_continuous(expand = c(0, 0)) +
  expand_limits(y = 0.01, x = 1.4) +
  theme(legend.position = c(0.03,0.12)) +
  theme(legend.title = element_text(face = "bold")) +
  theme(legend.title = element_text(size = 15)) +
  theme(legend.text = element_text(size = 15)) +
  ylab(expression(Condition~(g/cm^{"3"}))) + 
  theme(axis.title.x = element_text(margin = margin(t = 10))) +
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1)) +
  theme(axis.title.x = element_blank()) 


bsug_het_fitness_by_hybstatus_plot <- ggplot(bsug_het_fitness, aes(x = het, y = condition, fill = hyb_status)) + 
    geom_point(data = bsug_het_fitness_admix, size = 3, aes(x = het, y = condition, group = hyb_status, fill = hyb_status, shape = hyb_status), color = "black", pch = 21, show.legend = F) +
  geom_smooth(data = bsug_het_fitness_admix, aes(x = het, y = condition, color = hyb_status), show.legend = F, method = "lm", se=F, fullrange = T) +
  geom_point(data = bsug_het_fitness_neosho, size = 3, aes(x = het, y = condition, group = hyb_status, fill = hyb_status, shape = hyb_status), color = "black", pch = 22, show.legend = F) +
  geom_smooth(data = bsug_het_fitness_neosho, aes(x = het, y = condition, color = hyb_status), show.legend = F, method = "lm", se=F, fullrange = T) +
  geom_point(data = bsug_het_fitness_northern, size = 3, aes(x = het, y = condition, group = hyb_status, fill = hyb_status, shape = hyb_status), color = "black", pch = 24, show.legend = F) +
  geom_smooth(data = bsug_het_fitness_northern, aes(x = het, y = condition, color = hyb_status), show.legend = F, method = "lm", se=F, fullrange = T) +
  theme_set(theme_cowplot(12)) +
  labs(x = "Multilocus heterozygosity", y = "Body condition (g/cm3)") +
  theme(axis.title = element_text(size = 20)) +
  theme(axis.text = element_text(size = 15)) +
  scale_fill_manual(values = c("mediumpurple","deepskyblue2","deeppink2")) +
  scale_color_manual(values = c("mediumpurple","deepskyblue2","deeppink2")) +
  scale_shape_manual(values = c("circle","square","triangle")) +
  scale_x_continuous(expand = c(0, 0), breaks = seq(0,1.5,0.1)) + 
  scale_y_continuous(expand = c(0, 0)) +
  expand_limits(y = 0.01, x = 1.4) +
  ylab(expression(Condition~(g/cm^{"3"}))) + 
  theme(axis.title.x = element_text(margin = margin(t = 10))) +
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1)) +
  theme(axis.title.x = element_blank()) 


elk_het_fitness_by_hybstatus_plot <- ggplot(elk_het_fitness, aes(x = het, y = condition, fill = hyb_status)) + 
  geom_point(data = elk_het_fitness_admix, size = 3, aes(x = het, y = condition, group = hyb_status, fill = hyb_status, shape = hyb_status), color = "black", pch = 21, show.legend = F) +
  geom_smooth(data = elk_het_fitness_admix, aes(x = het, y = condition, color = hyb_status), show.legend = F, method = "lm", se=F, fullrange = T) +
  geom_point(data = elk_het_fitness_neosho, size = 3, aes(x = het, y = condition, group = hyb_status, fill = hyb_status, shape = hyb_status), color = "black", pch = 22, show.legend = F) +
  geom_smooth(data = elk_het_fitness_neosho, aes(x = het, y = condition, color = hyb_status), show.legend = F, method = "lm", se=F, fullrange = T) +
  geom_point(data = elk_het_fitness_northern, size = 3, aes(x = het, y = condition, group = hyb_status, fill = hyb_status, shape = hyb_status), color = "black", pch = 24, show.legend = F) +
  geom_smooth(data = elk_het_fitness_northern, aes(x = het, y = condition, color = hyb_status), show.legend = F, method = "lm", se=F, fullrange = T) +
  theme_set(theme_cowplot(12)) +
  labs(x = "Standardized multilocus heterozygosity", y = "Body condition (g/cm3)") +
  theme(axis.title = element_text(size = 20)) +
  theme(axis.text = element_text(size = 15)) +
  scale_fill_manual(values = c("mediumpurple","deepskyblue2","deeppink2")) +
  scale_color_manual(values = c("mediumpurple","deepskyblue2","deeppink2")) +
  scale_shape_manual(values = c("circle","square","triangle")) +
  scale_x_continuous(expand = c(0, 0), breaks = seq(0,1.5,0.1)) + 
  scale_y_continuous(expand = c(0, 0)) +
  expand_limits(y = 0.01, x = 1.4) +
  ylab(expression(Condition~(g/cm^{"3"}))) + 
  theme(axis.title.x = element_text(margin = margin(t = 10))) +
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1)) 
  


#Just the hybrid status HFCs together
pdf("/Users/joegunn/Desktop/Grad_School_Stuff/Research/Projects/Smallmouth_Bass_Fitness/visualization/hfc_plots/hfc_plots_by_hyb_status.pdf", width = 7, height = 15)

plot_grid(global_het_fitness_by_hybstatus_plot,
          bsug_het_fitness_by_hybstatus_plot,
          elk_het_fitness_by_hybstatus_plot,
          nrow = 3)

dev.off()


# Overall HFCs along with the individual hybrid status HFCs
pdf("/Users/joegunn/Desktop/Grad_School_Stuff/Research/Projects/Smallmouth_Bass_Fitness/visualization/hfc_plots/hfc_plots_all.pdf", width = 12, height = 15)

plot_grid(global_het_fitness_plot,
          global_het_fitness_by_hybstatus_plot,
          bsug_het_fitness_plot,
          bsug_het_fitness_by_hybstatus_plot,
          elk_het_fitness_plot,
          elk_het_fitness_by_hybstatus_plot,          
          nrow = 3)

dev.off()



ggplot(global_het_fitness, aes(x = hyb_status, y = condition)) +
  geom_boxplot(show.legend = F, outlier.shape = NA, alpha = 0.3) +
  geom_point(position = position_jitter(width = 0.1), size = 3, color = "black", pch = 21, show.legend = F)


global_het_fitness_admix <- global_het_fitness %>%
  filter(hyb_status == "Admixed")

global_het_fitness_northern <- global_het_fitness %>%
  filter(hyb_status == "Northern")

global_het_fitness_neosho <- global_het_fitness %>%
  filter(hyb_status == "Neosho")

bsug_het_fitness_admix <- bsug_het_fitness %>%
  filter(hyb_status == "Admixed")

bsug_het_fitness_northern <- bsug_het_fitness %>%
  filter(hyb_status == "Northern")

bsug_het_fitness_neosho <- bsug_het_fitness %>%
  filter(hyb_status == "Neosho")

elk_het_fitness_admix <- elk_het_fitness %>%
  filter(hyb_status == "Admixed")

elk_het_fitness_northern<- elk_het_fitness %>%
  filter(hyb_status == "Northern")

elk_het_fitness_neosho<- elk_het_fitness %>%
  filter(hyb_status == "Neosho")



global_het_fitness_ancova <- lme(condition ~ het*hyb_status, random = ~1|sex, global_het_fitness)
anova(global_het_fitness_ancova)

bsug_het_fitness_ancova <- lme(condition ~ het*hyb_status, random = ~1|sex, bsug_het_fitness)
anova(bsug_het_fitness_ancova)

elk_het_fitness_ancova <- lme(condition ~ het*hyb_status, random = ~1|sex, elk_het_fitness)
anova(elk_het_fitness_ancova)

```

## See if there is a difference in heterozygosity between pure and admixed samples
```{r}

# Read in genetic data with inbreed R
gen_data_with_refs_fit <- read_csv("../../raw_data/genotype_data/genotype_files/smbfit_msat_genotypes.csv")

ref_fit_data <- gen_data_with_refs_fit[,(2:4)]
ref_fit_data <- ref_fit_data %>%
  mutate(hyb_status = factor(hyb_status),
         pure_admix = factor(pure_admix),
         population = factor(population))

gen_data_with_refs <- gen_data_with_refs_fit[,-c(2:4)]
gen_data_with_refs <- column_to_rownames(gen_data_with_refs, "sample_id")

gen_data_with_refs_inbreedr <- convert_raw(gen_data_with_refs)
check_data(gen_data_with_refs_inbreedr)


het_all_with_ref <- as.data.frame(sMLH(gen_data_with_refs_inbreedr))
het_all_with_ref <- rownames_to_column(het_all_with_ref, "sample_id")
het_all_with_ref <- het_all_with_ref %>%
  mutate(sample_id = factor(sample_id))
colnames(het_all_with_ref) <- c("sample_id","het")


het_fit_with_ref <- cbind(ref_fit_data,het_all_with_ref)

levels(het_fit_with_ref$population) <- gsub(" ", "\n", levels(het_fit_with_ref$population))

het_by_hybrid_status <- ggplot(het_fit_with_ref, aes(x = population, y = het, fill = hyb_status)) + 
  geom_boxplot(show.legend = F, outlier.shape = NA, alpha = 0.3) +
  geom_point(position = position_jitterdodge(), size = 3, color = "black", pch = 21, show.legend = F) +
  theme_set(theme_cowplot(12)) + 
  labs(x = "River/Population", y = "Multi-locus heterozygosity") +
  scale_fill_manual(values = c("mediumpurple","deepskyblue2","deeppink2","grey","grey")) +
  theme(axis.title = element_text(size = 20)) +
  theme(axis.text = element_text(size = 15)) +
  theme(legend.position = c(0.75,0.2)) +
  expand_limits(y = 1) +
  theme(axis.title.x = element_text(margin = margin(t = 10))) +
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1))

het_by_population <- ggplot(het_fit_with_ref, aes(x = population, y = het, fill = "grey")) + 
  geom_boxplot(show.legend = F, outlier.shape = NA, alpha = 0.3) +
  geom_point(position = position_jitter(width = 0.1), size = 3, color = "black", pch = 21, show.legend = F) +
  theme_set(theme_cowplot(12)) + 
  labs(x = "River/Population", y = "Multi-locus heterozygosity") +
  scale_fill_manual(values = c("grey","grey","grey","grey")) +
  theme(axis.title = element_text(size = 20)) +
  theme(axis.text = element_text(size = 15)) +
  theme(legend.position = c(0.75,0.2)) +
  expand_limits(y = 1) +
  theme(axis.title.x = element_text(margin = margin(t = 10))) +
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1))


pdf("/Users/joegunn/Desktop/Grad_School_Stuff/Research/Projects/Smallmouth_Bass_Fitness/visualization/hfc_plots/het_comparison_ref_pops.pdf", width = 8, height = 10)


plot_grid(het_by_population, 
          het_by_hybrid_status,
          nrow = 2,
          labels = c("a","b"),
          label_size = 25,
          align = "v",
          label_y = 1.03)

dev.off()

## Run linear model
het_all_with_ref_lm <- lm(het ~ population, het_fit_with_ref)
summary(het_all_with_ref_lm)

post_het_ref <- glht(het_all_with_ref_lm, mcp(population = "Tukey"))
summary(post_het_ref)


het_all_with_ref_hyb_status_lm <- lm(het ~ hyb_status, het_fit_with_ref)
summary(het_all_with_ref_hyb_status_lm)

post_het_ref_hyb_status <- glht(het_all_with_ref_hyb_status_lm, mcp(hyb_status = "Tukey"))
summary(post_het_ref_hyb_status)

het_fit_with_ref$concatenate <- paste(het_fit_with_ref$hyb_status, het_fit_with_ref$population)
het_fit_with_ref <- het_fit_with_ref %>%
  mutate(concatenate = factor(concatenate))


het_all_with_ref_hyb_status_concatenate_lm <- lm(het ~ concatenate, het_fit_with_ref)
post_het_ref_hyb_status_concatenate <- glht(het_all_with_ref_hyb_status_concatenate_lm, mcp(concatenate = "Tukey"))
summary(post_het_ref_hyb_status_concatenate)

```

## Use all Neosho and Northern reference individuals
```{r}
# Read in genetic data with inbreed R
gen_data_all_refs <- read_csv("../../raw_data/genotype_data/genotype_files/smbfit_msat_genotypes_noHSYC_with_old_neosho.csv")

all_ref_fit_data <- gen_data_all_refs[,(2:4)]
all_ref_fit_data <- all_ref_fit_data %>%
  mutate(hyb_status = factor(hyb_status),
         pure_admix = factor(pure_admix),
         population = factor(population))

gen_data_with_all_refs <- gen_data_all_refs[,-c(2:4)]
gen_data_with_all_refs <- column_to_rownames(gen_data_with_all_refs, "sample_id")

gen_data_with_all_refs_inbreedr <- convert_raw(gen_data_with_all_refs)
check_data(gen_data_with_all_refs_inbreedr)


het_all_with_ref <- as.data.frame(sMLH(gen_data_with_all_refs_inbreedr))
het_all_with_ref <- rownames_to_column(het_all_with_ref, "sample_id")
het_all_with_ref <- het_all_with_ref %>%
  mutate(sample_id = factor(sample_id))
colnames(het_all_with_ref) <- c("sample_id","het")


het_fit_with_all_ref <- cbind(all_ref_fit_data, het_all_with_ref)

levels(het_fit_with_all_ref$population) <- gsub(" ", "\n", levels(het_fit_with_all_ref$population))

het_by_hybrid_status_all_refs <- ggplot(het_fit_with_all_ref, aes(x = population, y = het, fill = hyb_status)) + 
  geom_boxplot(show.legend = F, outlier.shape = NA, alpha = 0.3) +
  geom_point(position = position_jitterdodge(), size = 3, color = "black", pch = 21, show.legend = F) +
  theme_set(theme_cowplot(12)) + 
  labs(x = "River/Population", y = "Multi-locus heterozygosity") +
  scale_fill_manual(values = c("mediumpurple","deepskyblue2","deeppink2","grey","grey")) +
  theme(axis.title = element_text(size = 20)) +
  theme(axis.text = element_text(size = 15)) +
  theme(legend.position = c(0.75,0.2)) +
  expand_limits(y = 1) +
  theme(axis.title.x = element_text(margin = margin(t = 10))) +
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1))

het_by_population_all_refs <- ggplot(het_fit_with_all_ref, aes(x = population, y = het, fill = "grey")) + 
  geom_boxplot(show.legend = F, outlier.shape = NA, alpha = 0.3) +
  geom_point(position = position_jitter(width = 0.1), size = 3, color = "black", pch = 21, show.legend = F) +
  theme_set(theme_cowplot(12)) + 
  labs(x = "River/Population", y = "Multi-locus heterozygosity") +
  scale_fill_manual(values = c("grey","grey","grey","grey")) +
  theme(axis.title = element_text(size = 20)) +
  theme(axis.text = element_text(size = 15)) +
  theme(legend.position = c(0.75,0.2)) +
  expand_limits(y = 1) +
  theme(axis.title.x = element_text(margin = margin(t = 10))) +
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1))


pdf("/Users/joegunn/Desktop/Grad_School_Stuff/Research/Projects/Smallmouth_Bass_Fitness/visualization/hfc_plots/het_comparison_ref_pops.pdf", width = 8, height = 10)

plot_grid(het_by_population_all_refs, 
          het_by_hybrid_status_all_refs,
          nrow = 2,
          labels = c("a","b"),
          label_size = 25,
          align = "v",
          label_y = 1.03)

dev.off()

## Run linear model
het_all_with_all_ref_lm <- lm(het ~ population, het_fit_with_all_ref)
summary(het_all_with_all_ref_lm)

#overall p value < 0.001

post_het_all_ref <- glht(het_all_with_all_ref_lm, mcp(population = "Tukey"))
summary(post_het_all_ref)


het_all_with_all_ref_hyb_status_lm <- lm(het ~ hyb_status, het_fit_with_all_ref)
summary(het_all_with_all_ref_hyb_status_lm)

#overall p value < 0.001

post_het_all_ref_hyb_status <- glht(het_all_with_all_ref_hyb_status_lm, mcp(hyb_status = "Tukey"))
summary(post_het_all_ref_hyb_status)

het_fit_with_all_ref$concatenate <- paste(het_fit_with_all_ref$hyb_status, het_fit_with_all_ref$population)
het_fit_with_all_ref <- het_fit_with_all_ref %>%
  mutate(concatenate = factor(concatenate))


het_all_with_all_ref_hyb_status_concatenate_lm <- lm(het ~ concatenate, het_fit_with_all_ref)
post_het_all_ref_hyb_status_concatenate <- glht(het_all_with_all_ref_hyb_status_concatenate_lm, mcp(concatenate = "Tukey"))
summary(post_het_all_ref_hyb_status_concatenate)

```
## Here I am going to run all of the analyses assuming that I can keep all of my data, including the large, old samples

## Keep all ages in the data
```{r}

# Read in genetic data with inbreed R

all_ages_with_fitness <- merge(fitness_data, gen_data, by = "sample_id")

gen_data_all_ages <- all_ages_with_fitness[,-c(2:11)]
gen_data_all_ages <- column_to_rownames(gen_data_all_ages, "sample_id")

gen_data_inbreedr_all_ages <- convert_raw(gen_data_all_ages)
check_data(gen_data_inbreedr_all_ages)

gen_data_bsug_all_ages <- all_ages_with_fitness %>%
  filter(river == "BSUG")

gen_data_elk_all_ages <- all_ages_with_fitness %>%
  filter(river == "ELK")

gen_data_bsug_all_ages <- column_to_rownames(gen_data_bsug_all_ages, "sample_id")
gen_data_elk_all_ages <- column_to_rownames(gen_data_elk_all_ages, "sample_id")

gen_data_bsug_all_ages <- gen_data_bsug_all_ages[,-c(1:10)]
gen_data_elk_all_ages <- gen_data_elk_all_ages [,-c(1:10)]

gen_data_bsug_inbreedr_all_ages <- convert_raw(gen_data_bsug_all_ages)
check_data(gen_data_bsug_inbreedr_all_ages)

gen_data_elk_inbreedr_all_ages <- convert_raw(gen_data_elk_all_ages)
check_data(gen_data_elk_inbreedr_all_ages)

```

## Calcualte g2 coefficients for each dataset (g2 measures identity disequilibrium, which is a measure of how correlated heterozygosity is and tells you whether you have high power of detecting general effects of inbreeding across the genome (if high correlation among loci, then we assume that the rest of the genome is probably mostly heterozygous))
```{r}
g2_global_all_ages <- g2_microsats(gen_data_inbreedr_all_ages, nperm = 1000, nboot = 1000, CI = 0.95)
#p = 0.026, se = 0.006, 2.5% ci = 2.893e-05, 97.5% ci = 2.297e-02, g2 = 0.011

g2_bsug_all_ages <- g2_microsats(gen_data_bsug_inbreedr_all_ages, nperm = 1000, nboot = 1000, CI = 0.95)
#p = 0.291, se = 0.009, 2.5% ci = -0.012, 97.5% ci = 0.026, g2 = 0.005

g2_elk_all_ages <- g2_microsats(gen_data_elk_inbreedr_all_ages, nperm = 1000, nboot = 1000, CI = 0.95)
#p = 0.021, se = 0.007, 2.5% ci = 0.001, 97.5% ci = 0.030, g2 = 0.015
```

## Get heterozygosity measures per individual in each dataset
```{r}

het_global_all_ages <- as.data.frame(sMLH(gen_data_inbreedr_all_ages))
het_global_all_ages <- rownames_to_column(het_global_all_ages, "sample_id")
het_global_all_ages <- het_global_all_ages %>%
  mutate(sample_id = factor(sample_id))
colnames(het_global_all_ages) <- c("sample_id","het")

het_bsug_all_ages <- as.data.frame(sMLH(gen_data_bsug_inbreedr_all_ages))
het_bsug_all_ages <- rownames_to_column(het_bsug_all_ages, "sample_id")
het_bsug_all_ages <- het_bsug_all_ages %>%
  mutate(sample_id = factor(sample_id))
colnames(het_bsug_all_ages) <- c("sample_id","het")

het_elk_all_ages <- as.data.frame(sMLH(gen_data_elk_inbreedr_all_ages))
het_elk_all_ages <- rownames_to_column(het_elk_all_ages, "sample_id")
het_elk_all_ages <- het_elk_all_ages %>%
  mutate(sample_id = factor(sample_id))
colnames(het_elk_all_ages) <- c("sample_id","het")
 
global_het_fitness_all_ages <- merge(het_global_all_ages, fitness_data, by = "sample_id")
bsug_het_fitness_all_ages <- merge(het_bsug_all_ages, fitness_data, by = "sample_id")
elk_het_fitness_all_ages <- merge(het_elk_all_ages, fitness_data, by = "sample_id")

#plot condition by heterozygosity
global_het_fitness_all_ages_plot <- ggplot(global_het_fitness_all_ages, aes(x = het,y = condition)) + 
  geom_point(size = 2.5) +
  geom_smooth(method = "lm", se = T, color = "black") +
  theme_set(theme_cowplot(12)) +
  labs(x = "Heterozygosity", y = "Body condition (g/cm3)") +
  theme(axis.title = element_text(size = 20)) +
  theme(axis.text = element_text(size = 15)) +
  scale_x_continuous(expand = c(0, 0), breaks = seq(0,1.5,0.1)) + 
  scale_y_continuous(expand = c(0, 0)) +
  expand_limits(y = 0.01, x = 1.4) +
  theme(axis.title.x = element_text(margin = margin(t = 10))) +
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1))

 global_het_fitness_all_ages <- global_het_fitness_all_ages[-c(115),]

global_het_fitness_all_ages_lme <- lme(condition ~ het, random = ~1|sex,  global_het_fitness_all_ages)
anova.lme(global_het_fitness_all_ages_lme)
#p = 0.032, F = 4.72


bsug_het_fitness_all_ages_plot <- ggplot(bsug_het_fitness_all_ages, aes(x = het, y = condition)) + 
  geom_point(size = 2.5) +
  geom_smooth(method = "lm", se = T, color = "black") +
  theme_set(theme_cowplot(12)) +
  labs(x = "Heterozygosity", y = "Body condition (g/cm3)") +
  theme(axis.title = element_text(size = 20)) +
  theme(axis.text = element_text(size = 15)) +
  scale_x_continuous(expand = c(0, 0), breaks = seq(0,1.5,0.1)) + 
  scale_y_continuous(expand = c(0, 0)) +
  expand_limits(y = 0.01, x = 1.4) +
  theme(axis.title.x = element_text(margin = margin(t = 10))) +
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1))

bsug_het_fitness_all_ages_lme <- lme(condition ~ het, random = ~1|sex, bsug_het_fitness_all_ages)
anova.lme(bsug_het_fitness_all_ages_lme)
#p = 0.33, F = 0.956


elk_het_fitness_all_ages_plot <- ggplot(elk_het_fitness_all_ages, aes(x = het, y = condition)) + 
  geom_point(size = 2.5) +
  geom_smooth(method = "lm", se = T, color = "black") +
  theme_set(theme_cowplot(12)) +
  labs(x = "Heterozygosity", y = "Body condition (g/cm3)") +
  theme(axis.title = element_text(size = 20)) +
  theme(axis.text = element_text(size = 15)) +
  scale_x_continuous(expand = c(0, 0), breaks = seq(0,1.5,0.1)) + 
  scale_y_continuous(expand = c(0, 0)) +
  expand_limits(y = 0.01, x = 1.4) +
  theme(axis.title.x = element_text(margin = margin(t = 10))) +
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1))

elk_het_fitness_all_ages <- elk_het_fitness_all_ages[-c(70),]

elk_het_fitness_all_ages_lme <- lme(condition ~ het, random = ~1|sex, elk_het_fitness_all_ages)
anova.lme(elk_het_fitness_all_ages_lme)
#p = 0.050, F = 3.98
```