---
title: "SMB_Fitness_HFC"
author: "Joe Gunn"
date: "6/6/2021"
output: html_document
---

## Read in libraries needed for analysis
```{r, include=FALSE}
library(readxl)
library(tidyverse)
library(cowplot)
library(inbreedR)
library(nlme)
library(MuMIn)
library(bbmle)
library(lme4)
library(lmerTest)
```

## Read in and organize fitness data
```{r}

smbfit_raw_data <- read_excel("../../raw_data/master_data/smbfit_master_data_working.xlsx")

smbfit_raw_data_clean <- smbfit_raw_data %>%
  mutate(river = factor(river),
         tl_alive = as.numeric(tl_alive),
         tl_alive_cm = tl_alive/10,
         sex = factor(sex),
         hyb_status = factor(hyb_status),
         log_mass = log10(mass_g))

smbfit_raw_data_clean <- smbfit_raw_data_clean %>%
  mutate(condition = mass_g/(tl_alive_cm^3))

smbfit_mass_tl_data <- smbfit_raw_data_clean[,-c(2:4,6:8,10:11,13:17,19:23,25:40)]

smbfit_raw_data_clean_no_outlier <- smbfit_mass_tl_data[-c(13),]

fitness_data <- smbfit_raw_data_clean_no_outlier %>%
  mutate(sample_id = factor(sample_id)) %>%
  mutate(age_factor = factor(consensus_age))

fitness_data_4yo <- fitness_data %>%
  filter(consensus_age < 5) # 105 samples total that are less than 4 yo

fitness_data_4yo_bsug <- fitness_data_4yo %>%
  filter(river == "BSUG") #40

fitness_data_4yo_elk <- fitness_data_4yo %>%
  filter(river == "ELK") #65
```

## Assess body condition as a possible proxy for fitness, including how it is correlated with age
```{r}
##GLOBAL

#condition is calculated as mass divided by total length (cm) cubed, so it deals with both mass and length
 
#How does mass scale with length
global_mass_tl <- ggplot(fitness_data_4yo, aes(x = tl_alive, y = mass_g)) +
  geom_point(size = 2.5) +
  geom_smooth(method = "lm", se = F, color = "black") +
  theme_set(theme_cowplot(12)) +
  labs(x = "Total Length (mm)", y = "Mass (g)") +
  theme(axis.title = element_text(size = 20)) +
  theme(axis.text = element_text(size = 15)) +
  scale_x_continuous(expand = c(0, 0), breaks = seq(0,400,50)) + 
  scale_y_continuous(expand = c(0, 0)) +
  expand_limits(y = 700, x = 400) +
  theme(axis.title.x = element_text(margin = margin(t = 10))) +
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1)) +
  theme(axis.title.x = element_blank())
  
mass_by_tl_corr <- lm(mass_g ~ tl_alive, fitness_data_4yo)
summary(mass_by_tl_corr) #r2 = 0.937, p <0.001

#Is condition correlated with age?
global_age_condition <- ggplot(fitness_data_4yo, aes(x = consensus_age, y = condition)) +
  geom_point(size = 2.5, alpha = 0.5, position = position_jitter(width = 0.1)) +
  geom_smooth(method = "lm", se = F, color = "black") +
  theme_set(theme_cowplot(12)) +
  labs(x = "Age (years)", y = "Condition (g/cm3)") +
  theme(axis.title = element_text(size = 20)) +
  theme(axis.text = element_text(size = 15)) +
  scale_x_continuous(expand = c(0, 0), breaks = seq(0,4,1)) + 
  scale_y_continuous(expand = c(0, 0)) +
  expand_limits(y = 0.01, x = 4) +
  ylab(expression(Condition~(g/cm^{"3"}))) + 
  theme(axis.title.x = element_text(margin = margin(t = 10))) +
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1)) +
  theme(axis.title.x = element_blank())

condition_by_age_corr <- lm(condition ~ consensus_age, fitness_data_4yo)
summary(condition_by_age_corr) #r2 = 0.009, p = 0.346

#Is condition normally distributed?
global_condition_norm <- ggplot(fitness_data_4yo, aes(condition)) +
  geom_histogram(fill = "grey", color = "black") +
  theme_set(theme_cowplot(12)) +
  labs(x = "Condition (g/cm3)", y = "Frequency") +
  theme(axis.title = element_text(size = 20)) +
  theme(axis.text = element_text(size = 15)) +
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1)) +
  theme(axis.title.x = element_blank())

shapiro.test(fitness_data_4yo$condition)
#p = 0.4304, W = 0.969


##BIG SUGAR CREEK

#condition is calculated as mass divided by total length (cm) cubed, so it deals with both mass and length
 
#How does mass scale with length
bsug_mass_tl <- ggplot(fitness_data_4yo_bsug, aes(x = tl_alive, y = mass_g)) +
  geom_point(size = 2.5) +
  geom_smooth(method = "lm", se = F, color = "black") +
  theme_set(theme_cowplot(12)) +
  labs(x = "Total Length (mm)", y = "Mass (g)") +
  theme(axis.title = element_text(size = 20)) +
  theme(axis.text = element_text(size = 15)) +
  scale_x_continuous(expand = c(0, 0), breaks = seq(0,350,50)) + 
  scale_y_continuous(expand = c(0, 0)) +
  expand_limits(y = 600, x = 350) +
  theme(axis.title.x = element_text(margin = margin(t = 10))) +
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1)) +
  theme(axis.title.x = element_blank())
  
mass_by_tl_corr_bsug <- lm(mass_g ~ tl_alive, fitness_data_4yo_bsug)
summary(mass_by_tl_corr_bsug) #r2 = 0.94, p <0.001

#Is condition correlated with age?
bsug_age_condition <- ggplot(fitness_data_4yo_bsug, aes(x = consensus_age, y = condition)) +
  geom_point(size = 2.5, alpha = 0.5, position = position_jitter(width = 0.1)) +
  geom_smooth(method = "lm", se = F, color = "black") +
  theme_set(theme_cowplot(12)) +
  labs(x = "Age (years)", y = "Condition (g/cm3)") +
  theme(axis.title = element_text(size = 20)) +
  theme(axis.text = element_text(size = 15)) +
  scale_x_continuous(expand = c(0, 0), breaks = seq(0,4,1)) + 
  scale_y_continuous(expand = c(0, 0)) +
  expand_limits(y = 0.01, x = 4) +
  ylab(expression(Condition~(g/cm^{"3"}))) + 
  theme(axis.title.x = element_text(margin = margin(t = 10))) +
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1)) +
  theme(axis.title.x = element_blank())

condition_by_age_corr_bsug <- lm(condition ~ consensus_age, fitness_data_4yo_bsug)
summary(condition_by_age_corr_bsug) #r2 = 0.05, p = 0.147

#Is condition normally distributed?
bsug_condition_norm <- ggplot(fitness_data_4yo_bsug, aes(condition)) +
  geom_histogram(fill = "grey", color = "black") +
  theme_set(theme_cowplot(12)) +
  labs(x = "Condition (g/cm3)", y = "Frequency") +
  theme(axis.title = element_text(size = 20)) +
  theme(axis.text = element_text(size = 15)) +
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1)) +
  theme(axis.title.x = element_blank())

condition_norm_bsug <- shapiro.test(fitness_data_4yo_bsug$condition)
#p = 0.117, W = 0.955


##ELK RIVER

#condition is calculated as mass divided by total length (cm) cubed, so it deals with both mass and length
 
#How does mass scale with length
elk_mass_tl <- ggplot(fitness_data_4yo_elk, aes(x = tl_alive, y = mass_g)) +
  geom_point(size = 2.5) +
  geom_smooth(method = "lm", se = F, color = "black") +
  theme_set(theme_cowplot(12)) +
  labs(x = "Total Length (mm)", y = "Mass (g)") +
  theme(axis.title = element_text(size = 20)) +
  theme(axis.text = element_text(size = 15)) +
  scale_x_continuous(expand = c(0, 0), breaks = seq(0,350,50)) + 
  scale_y_continuous(expand = c(0, 0)) +
  expand_limits(y = 600, x = 350) +
  theme(axis.title.x = element_text(margin = margin(t = 10))) +
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1))
  
mass_by_tl_corr_elk <- lm(mass_g ~ tl_alive, fitness_data_4yo_elk)
summary(mass_by_tl_corr_elk) #r2 = 0.94, p <0.001

#Is condition correlated with age?
elk_age_condition <- ggplot(fitness_data_4yo_elk, aes(x = consensus_age, y = condition)) +
  geom_point(size = 2.5, alpha = 0.5, position = position_jitter(width = 0.1)) +
  geom_smooth(method = "lm", se = F, color = "black") +
  theme_set(theme_cowplot(12)) +
  labs(x = "Age (years)", y = "Condition (g/cm3)") +
  theme(axis.title = element_text(size = 20)) +
  theme(axis.text = element_text(size = 15)) +
  scale_x_continuous(expand = c(0, 0), breaks = seq(0,4,1)) + 
  scale_y_continuous(expand = c(0, 0)) +
  expand_limits(y = 0.01, x = 4) +
  ylab(expression(Condition~g/cm^{"3"})) + 
  theme(axis.title.x = element_text(margin = margin(t = 10))) +
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1))

condition_by_age_corr_elk <- lm(condition ~ consensus_age, fitness_data_4yo_elk)
summary(condition_by_age_corr_elk) #r2 = 0.001, p = 0.781

#Is condition normally distributed?
elk_condition_norm <- ggplot(fitness_data_4yo_elk, aes(condition)) +
  geom_histogram(fill = "grey", color = "black") +
  theme_set(theme_cowplot(12)) +
  labs(x = "Condition (g/cm^3)", y = "Frequency") +
  theme(axis.title = element_text(size = 20)) +
  theme(axis.text = element_text(size = 15)) +
  xlab(expression(Condition~(g/cm^{"3"}))) + 
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1))

condition_norm_elk <- shapiro.test(fitness_data_4yo_elk$condition)
#p = 0.181, W = 0.973

pdf("/Users/joegunn/Desktop/Grad_School_Stuff/Research/Projects/Smallmouth_Bass_Fitness/visualization/hfc_plots/condition_check_plots.pdf", width = 13, height = 10)

plot_grid(global_mass_tl, 
         global_age_condition, 
         global_condition_norm,
         bsug_mass_tl, 
         bsug_age_condition, 
         bsug_condition_norm,
         elk_mass_tl, 
         elk_age_condition, 
         elk_condition_norm,
         nrow = 3,
         labels = c("a","b","c","d","e","f","g","h","i"),
         label_size = 25,
         label_y = 1.04)

dev.off()
```

##Read in genetic data, and convert to inbreedR format for the global dataset, the big sugar dataset, and the elk river dataset
```{r}
# Read in genetic data with inbreed R
gen_data <- read_csv("../../raw_data/genotype_data/genotype_files/smbfit_msat_genotypes_noHSYC.csv")

gen_data_all_with_fitness <- merge(fitness_data_4yo, gen_data, by = "sample_id")

gen_data_all <- gen_data_all_with_fitness[,-c(2:11)]
gen_data_all <- column_to_rownames(gen_data_all, "sample_id")

gen_data_inbreedr <- convert_raw(gen_data_all)
check_data(gen_data_inbreedr)

gen_data_bsug_with_fitness <- gen_data_all_with_fitness %>%
  filter(river == "BSUG")

gen_data_elk_with_fitness <- gen_data_all_with_fitness %>%
  filter(river == "ELK")

gen_data_bsug_with_fitness <- column_to_rownames(gen_data_bsug_with_fitness, "sample_id")
gen_data_elk_with_fitness <- column_to_rownames(gen_data_elk_with_fitness, "sample_id")

gen_data_bsug <- gen_data_bsug_with_fitness[,-c(1:10)]
gen_data_elk <- gen_data_elk_with_fitness[,-c(1:10)]

gen_data_bsug_inbreedr <- convert_raw(gen_data_bsug)
check_data(gen_data_bsug_inbreedr)

gen_data_elk_inbreedr <- convert_raw(gen_data_elk)
check_data(gen_data_elk_inbreedr)
```

## Calcualte g2 coefficients for each dataset (g2 measures identity disequilibrium, which is a measure of how correlated heterozygosity is and tells you whether you have high power of detecting general effects of inbreeding across the genome (if high correlation among loci, then we assume that the rest of the genome is probably mostly heterozygous))
```{r}
g2_global <- g2_microsats(gen_data_inbreedr, nperm = 1000, nboot = 1000, CI = 0.95)
#p = 0.04, se = 0.006, 2.5% ci = -0.001, 97.5% ci = 0.233, g2 = 0.010

g2_bsug <- g2_microsats(gen_data_bsug_inbreedr, nperm = 1000, nboot = 1000, CI = 0.95)
#p = 0.377, se = 0.009, 2.5% ci = -0.014, 97.5% ci = 0.024, g2 = 0.002

g2_elk <- g2_microsats(gen_data_elk_inbreedr, nperm = 1000, nboot = 1000, CI = 0.95)
#p = 0.025, se = 0.008, 2.5% ci = 0.0005, 97.5% ci = 0.030, g2 = 0.015
```

## Get heterozygosity measures per individual in each dataset
```{r}

het_global <- as.data.frame(sMLH(gen_data_inbreedr))
het_global <- rownames_to_column(het_global, "sample_id")
het_global <- het_global %>%
  mutate(sample_id = factor(sample_id))
colnames(het_global) <- c("sample_id","het")

het_bsug <- as.data.frame(sMLH(gen_data_bsug_inbreedr))
het_bsug <- rownames_to_column(het_bsug, "sample_id")
het_bsug <- het_bsug %>%
  mutate(sample_id = factor(sample_id))
colnames(het_bsug) <- c("sample_id","het")

het_elk <- as.data.frame(sMLH(gen_data_elk_inbreedr))
het_elk <- rownames_to_column(het_elk, "sample_id")
het_elk <- het_elk %>%
  mutate(sample_id = factor(sample_id))
colnames(het_elk) <- c("sample_id","het")
 
global_het_fitness <- merge(het_global, fitness_data_4yo, by = "sample_id")
bsug_het_fitness <- merge(het_bsug, fitness_data_4yo_bsug, by = "sample_id")
elk_het_fitness <- merge(het_elk, fitness_data_4yo_elk, by = "sample_id")

#plot condition by heterozygosity
global_het_fitness_plot <- ggplot(global_het_fitness, aes(x = het,y = condition)) + 
  geom_point(size = 2.5) +
  geom_smooth(method = "lm", se = F, color = "black") +
  theme_set(theme_cowplot(12)) +
  labs(x = "Multilocus heterozygosity", y = "Body condition (g/cm3)") +
  theme(axis.title = element_text(size = 20)) +
  theme(axis.text = element_text(size = 15)) +
  scale_x_continuous(expand = c(0, 0), breaks = seq(0,1.5,0.1)) + 
  scale_y_continuous(expand = c(0, 0)) +
  expand_limits(y = 0.01, x = 1.4) +
  ylab(expression(Condition~(g/cm^{"3"}))) + 
  theme(axis.title.x = element_text(margin = margin(t = 10))) +
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1))

global_het_fitness <- global_het_fitness[-c(105),]

global_het_fitness_lme <- lme(condition ~ het, random = ~1|sex, global_het_fitness)
anova.lme(global_het_fitness_lme)
r.squaredGLMM(global_het_fitness_lme)
#p = 0.032, F = 4.75


bsug_het_fitness_plot <- ggplot(bsug_het_fitness, aes(x = het, y = condition)) + 
  geom_point(size = 2.5) +
  geom_smooth(method = "lm", se = F, color = "black") +
  theme_set(theme_cowplot(12)) +
  labs(x = "Multilocus heterozygosity", y = "Body condition (g/cm3)") +
  theme(axis.title = element_text(size = 20)) +
  theme(axis.text = element_text(size = 15)) +
  scale_x_continuous(expand = c(0, 0), breaks = seq(0,1.5,0.1)) + 
  scale_y_continuous(expand = c(0, 0)) +
  expand_limits(y = 0.01, x = 1.4) +
  ylab(expression(Condition~(g/cm^{"3"}))) + 
  theme(axis.title.x = element_text(margin = margin(t = 10))) +
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1)) +
  theme(axis.title.y = element_blank())

bsug_het_fitness_lme <- lme(condition ~ het, random = ~1|sex, bsug_het_fitness)
anova.lme(bsug_het_fitness_lme)
r.squaredGLMM(bsug_het_fitness_lme)
#p = 0.206, F = 1.65


elk_het_fitness_plot <- ggplot(elk_het_fitness, aes(x = het, y = condition)) + 
  geom_point(size = 2.5) +
  geom_smooth(method = "lm", se = F, color = "black") +
  theme_set(theme_cowplot(12)) +
  labs(x = "Multilocus heterozygosity", y = "Body condition (g/cm3)") +
  theme(axis.title = element_text(size = 20)) +
  theme(axis.text = element_text(size = 15)) +
  scale_x_continuous(expand = c(0, 0), breaks = seq(0,1.5,0.1)) + 
  scale_y_continuous(expand = c(0, 0)) +
  expand_limits(y = 0.01, x = 1.4) +
  ylab(expression(Condition~(g/cm^{"3"}))) + 
  theme(axis.title.x = element_text(margin = margin(t = 10))) +
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1)) +
  theme(axis.title.y = element_blank())
 
elk_het_fitness <- elk_het_fitness[-c(65),]

elk_het_fitness_lme <- lme(condition ~ het, random = ~1|sex, elk_het_fitness)
anova.lme(elk_het_fitness_lme)
r.squaredGLMM(elk_het_fitness_lme)
#p = 0.07, F = 3.45

pdf("/Users/joegunn/Desktop/Grad_School_Stuff/Research/Projects/Smallmouth_Bass_Fitness/visualization/hfc_plots/hfc_plots.pdf", width = 15, height = 5)

plot_grid(global_het_fitness_plot,
          bsug_het_fitness_plot,
          elk_het_fitness_plot,
          nrow = 1)

dev.off()


```


## Keep all ages in teh data
```{r}

# Read in genetic data with inbreed R

all_ages_with_fitness <- merge(fitness_data, gen_data, by = "sample_id")

gen_data_all_ages <- all_ages_with_fitness[,-c(2:11)]
gen_data_all_ages <- column_to_rownames(gen_data_all_ages, "sample_id")

gen_data_inbreedr_all_ages <- convert_raw(gen_data_all_ages)
check_data(gen_data_inbreedr_all_ages)

gen_data_bsug_all_ages <- all_ages_with_fitness %>%
  filter(river == "BSUG")

gen_data_elk_all_ages <- all_ages_with_fitness %>%
  filter(river == "ELK")

gen_data_bsug_all_ages <- column_to_rownames(gen_data_bsug_all_ages, "sample_id")
gen_data_elk_all_ages <- column_to_rownames(gen_data_elk_all_ages, "sample_id")

gen_data_bsug_all_ages <- gen_data_bsug_all_ages[,-c(1:10)]
gen_data_elk_all_ages <- gen_data_elk_all_ages [,-c(1:10)]

gen_data_bsug_inbreedr_all_ages <- convert_raw(gen_data_bsug_all_ages)
check_data(gen_data_bsug_inbreedr_all_ages)

gen_data_elk_inbreedr_all_ages <- convert_raw(gen_data_elk_all_ages)
check_data(gen_data_elk_inbreedr_all_ages)

```

## Calcualte g2 coefficients for each dataset (g2 measures identity disequilibrium, which is a measure of how correlated heterozygosity is and tells you whether you have high power of detecting general effects of inbreeding across the genome (if high correlation among loci, then we assume that the rest of the genome is probably mostly heterozygous))
```{r}
g2_global_all_ages <- g2_microsats(gen_data_inbreedr_all_ages, nperm = 1000, nboot = 1000, CI = 0.95)
#p = 0.026, se = 0.006, 2.5% ci = 2.893e-05, 97.5% ci = 2.297e-02, g2 = 0.011

g2_bsug_all_ages <- g2_microsats(gen_data_bsug_inbreedr_all_ages, nperm = 1000, nboot = 1000, CI = 0.95)
#p = 0.291, se = 0.009, 2.5% ci = -0.012, 97.5% ci = 0.026, g2 = 0.005

g2_elk_all_ages <- g2_microsats(gen_data_elk_inbreedr_all_ages, nperm = 1000, nboot = 1000, CI = 0.95)
#p = 0.021, se = 0.007, 2.5% ci = 0.001, 97.5% ci = 0.030, g2 = 0.015
```

## Get heterozygosity measures per individual in each dataset
```{r}

het_global_all_ages <- as.data.frame(sMLH(gen_data_inbreedr_all_ages))
het_global_all_ages <- rownames_to_column(het_global_all_ages, "sample_id")
het_global_all_ages <- het_global_all_ages %>%
  mutate(sample_id = factor(sample_id))
colnames(het_global_all_ages) <- c("sample_id","het")

het_bsug_all_ages <- as.data.frame(sMLH(gen_data_bsug_inbreedr_all_ages))
het_bsug_all_ages <- rownames_to_column(het_bsug_all_ages, "sample_id")
het_bsug_all_ages <- het_bsug_all_ages %>%
  mutate(sample_id = factor(sample_id))
colnames(het_bsug_all_ages) <- c("sample_id","het")

het_elk_all_ages <- as.data.frame(sMLH(gen_data_elk_inbreedr_all_ages))
het_elk_all_ages <- rownames_to_column(het_elk_all_ages, "sample_id")
het_elk_all_ages <- het_elk_all_ages %>%
  mutate(sample_id = factor(sample_id))
colnames(het_elk_all_ages) <- c("sample_id","het")
 
global_het_fitness_all_ages <- merge(het_global_all_ages, fitness_data, by = "sample_id")
bsug_het_fitness_all_ages <- merge(het_bsug_all_ages, fitness_data, by = "sample_id")
elk_het_fitness_all_ages <- merge(het_elk_all_ages, fitness_data, by = "sample_id")

#plot condition by heterozygosity
global_het_fitness_all_ages_plot <- ggplot(global_het_fitness_all_ages, aes(x = het,y = condition)) + 
  geom_point(size = 2.5) +
  geom_smooth(method = "lm", se = T, color = "black") +
  theme_set(theme_cowplot(12)) +
  labs(x = "Heterozygosity", y = "Body condition (g/cm3)") +
  theme(axis.title = element_text(size = 20)) +
  theme(axis.text = element_text(size = 15)) +
  scale_x_continuous(expand = c(0, 0), breaks = seq(0,1.5,0.1)) + 
  scale_y_continuous(expand = c(0, 0)) +
  expand_limits(y = 0.01, x = 1.4) +
  theme(axis.title.x = element_text(margin = margin(t = 10))) +
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1))

 global_het_fitness_all_ages <- global_het_fitness_all_ages[-c(115),]

global_het_fitness_all_ages_lme <- lme(condition ~ het, random = ~1|sex,  global_het_fitness_all_ages)
anova.lme(global_het_fitness_all_ages_lme)
#p = 0.032, F = 4.72


bsug_het_fitness_all_ages_plot <- ggplot(bsug_het_fitness_all_ages, aes(x = het, y = condition)) + 
  geom_point(size = 2.5) +
  geom_smooth(method = "lm", se = T, color = "black") +
  theme_set(theme_cowplot(12)) +
  labs(x = "Heterozygosity", y = "Body condition (g/cm3)") +
  theme(axis.title = element_text(size = 20)) +
  theme(axis.text = element_text(size = 15)) +
  scale_x_continuous(expand = c(0, 0), breaks = seq(0,1.5,0.1)) + 
  scale_y_continuous(expand = c(0, 0)) +
  expand_limits(y = 0.01, x = 1.4) +
  theme(axis.title.x = element_text(margin = margin(t = 10))) +
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1))

bsug_het_fitness_all_ages_lme <- lme(condition ~ het, random = ~1|sex, bsug_het_fitness_all_ages)
anova.lme(bsug_het_fitness_all_ages_lme)
#p = 0.33, F = 0.956


elk_het_fitness_all_ages_plot <- ggplot(elk_het_fitness_all_ages, aes(x = het, y = condition)) + 
  geom_point(size = 2.5) +
  geom_smooth(method = "lm", se = T, color = "black") +
  theme_set(theme_cowplot(12)) +
  labs(x = "Heterozygosity", y = "Body condition (g/cm3)") +
  theme(axis.title = element_text(size = 20)) +
  theme(axis.text = element_text(size = 15)) +
  scale_x_continuous(expand = c(0, 0), breaks = seq(0,1.5,0.1)) + 
  scale_y_continuous(expand = c(0, 0)) +
  expand_limits(y = 0.01, x = 1.4) +
  theme(axis.title.x = element_text(margin = margin(t = 10))) +
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1))

elk_het_fitness_all_ages <- elk_het_fitness_all_ages[-c(70),]

elk_het_fitness_all_ages_lme <- lme(condition ~ het, random = ~1|sex, elk_het_fitness_all_ages)
anova.lme(elk_het_fitness_all_ages_lme)
#p = 0.050, F = 3.98
```